\chapter{Stokes Structures}\label{chap:stokes}
Stokes structures are contain exactly \rewrite{necessary information} to
classify meromorphic classification, i.e.\ with the Stokes structures we are
able to construct a \rewrite{space}, which is isomorphic to the classifying
\rewrite{set}.

A great overview of this topic is given by Varadarajan in
\cite{Varadarajan96linearmeromorphic}. Other resources we will use are for
example \rewrite{Sabbah's} book \cite[section II]{sabbah2007isomonodromic} for
section~\ref{sec:mainThm1}.
For the sections~\ref{sec:StokesGroup} and~\ref{sec:mainThm2} will
\rewrite{Loday-Richaud's} paper \cite{Loday1994} and the book
\cite[Sec.4]{Loday2014} be \rewrite{useful. Also useful} was \rewrite{Boalch's}
paper \cite{boalch} (resp.\ his thesis \cite{thboalch}) which looks only at the
single leveled case.

Let $(\cM^{nf},\nabla^{nf})$ be a fixed model with the corresponding normal
form $A^0$.  The first objective is to proof the Malgrange-Sibuya theorem
in section~\ref{sec:mainThm1}. It states that the classifying set $\cH(A^0)$
is via an map $\exp$ isomorphic to the first cohomology
$H^1(S^1;\Lambda(A^0))=:\St(A^0)$.
In section~\ref{sec:mainThm2} we will improve the Malgrange-Sibuya Theorem by
showing that each 1-cohomology class in $\St(A^0)$ contains a unique
$1$-cocycle of a special form called \emph{the Stokes cocycle}
(cf.\ Section~\ref{sec:StokesGroup}).
The morphism, which maps each Stokes cocycle to its corresponding $1$-cocycle
will be denoted by $h$.

This will be further improved in section~\ref{sec:furtherImprovements}.

We \rewrite{have the following} commutative diagram of isomorphisms.
\begin{center}
  \begin{tikzpicture}[scale=3]
    \node[] (modSpcMat) at (0,0) {$\cH(\cM^{nf},\nabla^{nf})$};
    \node[blue] (mat) at (0,-1.3) {$\prod_{\theta\in\A}\Sto_\theta(A^0)$};
    \node[purple] (class) at ($(modSpcMat)!0.3!(mat)$) {$\cH(A^0)$};
    \node[green!40!black] (sheaf) at (3,0) {$\St(\cM^{nf})$};
    \node[] (sheaf3) at ($(sheaf)!0.3!(mat)$) {\textcolor{purple}{$\St(A^0)$}};
    % \node[blue] (mat') at (3.5,-1.5) {$(U_+\times U_-)^{k-1}$};

    % \draw[thick,double] (modSpcMat) -- (modSpcSheaf) -- (class) -- (class2) --
    %   (modSpcMat);
    \draw[thick,double,blue] (modSpcMat) -- (class);
    \draw[purple,thick,double] (sheaf) -- (sheaf3);

    \draw[->,green!40!black] (modSpcMat) -- (sheaf)
      node[midway,above] {$\exp$};
%    \draw[->,blue,dashed] (modSpcMat) edge[bend right=20] (mat);
    \draw[->,blue] (class) -- (mat) node[midway,left] {g};
    % \draw[->,blue,dotted] (mat) -- (mat') node[midway,right] {$\cK=\{k-1\}$};
    \draw[->,purple,dashed] (class) -- (sheaf3)
      node[midway,below] {$\exp_{A^0}$};
    % \draw[->,purple,dashed] (class) -- (mat);
    \draw[->,purple] (mat) -- (sheaf3) node[midway, below right] {$h$};
%    \draw[->,purple,dashed] (sheaf3) edge[bend right=20] (mat);
  \end{tikzpicture}
\end{center}\label{page:ofPreDiagram}
The map $g$, which makes the diagram commute, is defined using the theory of
summation, which will be roughly discussed the appendix in
section~\ref{sec:multisummability}.
This diagram will be enhanced in section~\ref{sec:theCompleteDiagram} by
adding a couple of isomorphisms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stokes structures: Malgrange-Sibuya isomorphism}\label{sec:mainThm1}
\marginnote{\cite[Thm.I.2.1]{Loday1994},
  \\\cite[Thm.4.3.9]{Loday2014},
  \\\cite[Thm.II.6.2]{sabbah2007isomonodromic}}
Here we will look at the classifying set and we will proof that it is
isomorphic \TODO[as\dots] to the first non abelian cohomology \rewrite{set}
$H^1(S^1;\Lambda(A^0))=:\St(A^0)$.
If we talk about cocycles or cochains, we will in the following always mean
$1$-cocycles or $1$-cochains.

Let us first define the Stokes sheaf $\Lambda(A^0)$ on $S^1$, as the sheaf of
flat isotropies of $[A^0]$.
\begin{defn}\label{defn:StokesSheaf}
  \begin{comment}
    The Stokes sheaf $\Lambda(A^0)$ of $A^0$, is the sheaf of groups defined on
    $S^1$ whose stalk at any point $\theta\in S^1$ is the group of germs of
    $f\in\Gl_n(\cO(\mathfrak{s}))$, $\mathfrak{s}$ a sector containing
    $\theta$, satisfying the conditions:
    \begin{enumerate}
      \item Flatness:
        $\underset{x\in\mathfrak{s}}{\underset{x\to0}{\lim}}f(x)=1$ and
        $f\sim_{\mathfrak{s}} 1$;
        \PROBLEM[Why two condition?]
      \item Isotropy of $A^0$: ${}^f\!A^0=A^0$.
    \end{enumerate}
  \end{comment}
  The Stokes sheaf $\Lambda(A^0)$ of $A^0$, is defined as the subsheaf of
  $\GL_n(\cA)$, in the following way.
  For some $\theta\in S^1$ is the stalk at $\theta$ the subgroup of
  $\GL_n(\cA)_\theta$ of elements $f$ which satisfy
  \begin{enumerate}
    \item Multiplicatively flatness: $f$ is asymptotic to the identity,
      i.e.\ $f\sim_{\mathfrak{s}} 1$;
    \item Isotropy of $A^0$: ${}^f\!A^0=A^0$.
  \end{enumerate}
  \begin{s-rem}
    This definition \rewrite{makes also sense as} $\Lambda(A)$ where $A$ stands
    for a systems wich is not in normal form.
  \end{s-rem}
  \begin{comment}
    \begin{s-rem}
      \PROBLEM[remove? need more defs!]
      Sabbah \cite[110]{sabbah2007isomonodromic} talks about (global)
      meromorphic connections $\sM$ on a small disk $D$ around $0$ instead of
      germs of meromorphic connections.

      Define on $S^1$ the sheaf $\Aut^{<0}(\tilde\sM^{nf})$ of automorphisms of
      $\tilde\sM^{nf}:=\cA_D\otimes_{\cO_D}\sM^{nf}$ which
      \begin{itemize}
        \item are compatible with the connection and
        \item are formally equal to the identity, i.e.\ induce the identity on
          $\hat\sM^{nf}:=\hat\cO_D\otimes_{\cO_D}\sM^{nf}$
      \end{itemize}

      The sheaf $\Aut^{<0}(\tilde\sM^{nf})$ corresponds to our $\Lambda(A^0)$.
    \end{s-rem}
  \end{comment}
\end{defn}

\subsection{The theorem}
In the language of meromorphic connections is the map, in the Malgrange-Sibuya
Theorem bellow, described as follows.

Let $(\cM,\nabla,\hat f)$ be a marked germ of a  meromorphic connection.
\rewrite{By Theorem}~\ref{thm:maet} there exists an open covering
$\cU=(U_j)_{j\in J}$ and for every open set, an isomorphism
\[
  f_j:(\tilde\cM,\tilde\nabla)_{|U_j}
  \to(\tilde\cM^{nf},\tilde\nabla^{nf})_{|U_j}
\]
such that $f_j\sim_{U_j}\hat f$.
By $(f_kf_j^{-1})_{jk}$ is then a cocycle of the sheaf $\St(A^0)$, relative
to the covering $\cU$, defined.
\comm{For other lifts $f_j'$ of $\hat f$ on $W_j$, $(f_j'f_j^{-1})$ is a
  $0$-cochain of $\Sto(A^0)$ relative to $\cU$. Thus the associated cochians to
  $(f_j)$ and $(f_j')$ are equivalent. One can also check that, if
  $(\cM,\nabla,\hat f)$ and $(\cM',\nabla',\hat f')$ are isomorphic, the
  corresponding cocycles define the same cohomology class.}
This defines a mapping of pointed sets
\[
  \exp:\cH(\cM^{nf},\nabla^{nf})\longrightarrow H^1(S^1;\Lambda(A^0))
\]
to the first non abelian cohomology of $\Lambda(A^0)$, which sends the class of
$(\cM^{nf},\nabla^{nf},\hat\id)$ to that of $\id$, i.e.\ the trivial cohomology
class.

\begin{center}
  \begin{minipage}[t]{0.8\textwidth}
    \begin{tthm}[Malgrange-Sibuya] \label{thm:mainThm1MeromVersion}
      \marginnote{\cite[Thm.I.4.5.1]{babbitt1989local},
        \\\cite[Thm.3.4]{Malgrange1983},
        \\\cite[Thm.13]{Martinet1991}}
      The homomorphism
      \[ \begin{tikzcd}
          \exp:\cH(\cM^{nf},\nabla^{nf}) \rar& \St(A^0):=H^1(S^1;\Lambda(A^0))
      \end{tikzcd} \]
      is an isomorphism of pointed sets.
    \end{tthm}
  \end{minipage}
\end{center}

\subsubsection{The theorem (system version)}
Since the language of meromorphic connections is equivalent to the one of
systems, there is also the translated version of the Malgrange-Sibuya
isomorphism to the language of systems. The corresponding map is then build as
follows.

\marginnote{\cite[855]{Loday1994}}
Let $(A,\hat F)$ be a marked pair, thus $\hat F$ solves $[A^0,A]$.
By the M.A.E.T there exists an open covering $\cU=(U_j)_{j\in J}$ together
with, for every open set $U_j$ a lift $F_j\in\Gl_n(\cA(U_j))$ of $\hat F$
(cf.\ Definition~\ref{defn:lift}), which solves $[A,A^0]$.
By the cocycle $(F_l^{-1}F_j)_{jl}\in\Gamma(\dot\cU;\Lambda(A^0))$ is then a
cohomology class in $\St(A^0)$, relative to the covering $\cU$, determined.
For other lifts $F_j'$ of $\hat F$ on $U_j$ is $(G_j=F_j^{-1}F_j')$ a
$0$-cochain of $\Lambda(A^0)$ relative to $\cU$, which satisfies
\[
  F_k^{-1}F_j=G_k F_k'^{-1}F'_j G_j^{-1} \,.
\]
Thus the cochians associated to $(F_j)$ and $(F_j')$ determine the same
cohomology class in $\St(A^0)$.
One can also check that, if $(A,\hat F)$ and $(A',\hat F')$ are equivalent, the
corresponding cocycles define the same cohomology class.
This defines a welldefined mapping of pointed sets
\[
  \cH(A^0)\to H^1(S^1;\Lambda(A^0))
\]
to the first non abelian cohomology of $\Lambda(A^0)$, which we call $\exp$.
It maps the class of $(A^0,\hat\id)$ to that of $\id$, i.e.\ the trivial
cohomology class.

\begin{center}
  \begin{minipage}[t]{0.8\textwidth}
    \begin{tthm}[Malgrange-Sibuya \rewrite{(system version)}]\label{thm:mainThm1}
      \marginnote{\cite[Theorem 4.5.1]{babbitt1989local}}
      The homomorphism
      \[ \begin{tikzcd}
          \exp:\cH(A^0) \rar& \St(A^0):=H^1(S^1;\Lambda(A^0))
      \end{tikzcd} \]
      is an isomorphism of pointed sets.
    \end{tthm}
  \end{minipage}
\end{center}
\begin{rem}
  % \TODO[Frage Felix!]
  The theorem \cite[Thm.III.1.1.2]{babbitt1989local}, in the book from
  Babbitt and Varadarajan, states that $\St(A^0)$ is actually a local moduli
  space for marked pairs, which are formally isomorphic to a given system
  $[A^0]$.
  \begin{comment}
    This means that
    \begin{itemize}
      \item the morphism property,
      \item the criterion of equivalence and
      \item the existence of universal families
    \end{itemize}
    are satisfied (cf.\ \cite[169]{babbitt1989local}).
  \end{comment}
  In fact is the whole third part of \cite{babbitt1989local} dedicated to this
  topic.
\end{rem}
Since the morphism $\exp$ depends on the choice of the normal form, we will
denote that, if it is not clear, by $\exp_{A^0}=\exp$\comm{~(In Loday-Richaud's
paper is this denoted as $\exp_{\mu_0}$)}.
\begin{rem}\label{rem:expNonNormalForm}
  \marginnote{\cite{Loday1994} Remark I.2.2}
  To another normal form $A^1={}^\Phi\!A^0$ there correspond cochains, which
  are conjugated via $\Phi$.
  We get the following commutative diagram:
  \begin{center}
    \begin{tikzpicture}[scale=2.6]
      \node (tl) at (-1,0.6) {$G\backslash\hat G(A^1)$};
      \node (tr) at (1,0.6) {$G\backslash\hat G(A^0)$};
      \node (bl) at (-1,-0.6) {$H^1(S^1;\lambda(A^1))$};
      \node (br) at (1,-0.6) {$H^1(S^1;\lambda(A^0))$};
      \node (tlin) at ($ (tl) - (-0.3,0.2) $)
        {\rotatebox[origin=c]{135}{$\in$}};
      \node (trin) at ($ (tr) - (-0.3,0.2) $)
        {\rotatebox[origin=c]{135}{$\in$}};
      \node (blin) at ($ (bl) - (-0.2,0.2) $)
        {\rotatebox[origin=c]{135}{$\in$}};
      \node (brin) at ($ (br) - (-0.2,0.2) $)
        {\rotatebox[origin=c]{135}{$\in$}};
      \node (tlE) at ($ (tl) - (-0.5,0.4) $) {$\hat F$};
      \node (trE) at ($ (tr) - (-0.5,0.4) $) {$\hat F\Phi$};
      \node (blE) at ($ (bl) - (-0.5,0.4) $) {$\exp_{A^1}(\hat F)$};
      \node (brE) at ($ (br) - (-0.5,0.4) $) {$\exp_{A^0}(\hat F\Phi)$};
      \draw[->] (tl) -- (tr) node [midway,above] {$\cdot\Phi$};
      \draw[->] (tl) -- (bl) node [midway,right] {$\exp_{A^1}$};
      \draw[->] (tr) -- (br) node [midway,right] {$\exp_{A^0}$};
      \draw[->] (bl) -- (br);
      \draw[|->] (tlE) -- (trE);
      \draw[|->] (tlE) -- (blE);
      \draw[|->] (trE) -- (brE);
      \draw[|->] (blE) -- (brE);
    \end{tikzpicture}
  \end{center}
  where $\exp_{A^0}(\hat F\Phi)=\Phi^{-1}\exp_{A^0}(\hat F)\Phi$.
  \TODO[$\Phi\in G(\!(t)\!)$???]
\end{rem}

\subsection{Proof of Theorem~\ref{thm:mainThm1}}
We will mainly refer to \cite[Proof of Theorem 4.5.1]{babbitt1989local} and
\cite[Section 6.d]{sabbah2007isomonodromic}, where a slightly more complicated
case with deformation space is proofen. These both resources proof the theorem
using the languages of meromorphic connections whereas we will use systems.
\marginnote{See also \cite{BJL1979Birkhoff} and \cite{babbitt1989local}
  although the proof goes back to work from Malgrange and Sibuya (see for
  example \cite{sibuya1990Linear}).}

We will start by proofing the injectivity of the morphism $\exp$.
\begin{proof}[Proof of the injectivity]
  % \textbf{First look at injectivity:}
  Consider the two marked pairs $(A,\hat F)$ and $(A',\hat F')$ in
  $\hat\Syst_m(A^0)$, whose classes in $\cH(A^0)$ get mapped to same element
  \[
    \exp((A,\hat F))=\lambda=\exp((A',\hat F'))
      \in H^1(S^1;\Lambda(A^0)) \,.
  \]
  By using refined coverings, it is possible to find a finite covering
  $\cU=\{U_j;j\in J\}$ of $S^1$ such that $\lambda$ is the class of the
  cocycles $(F_l^{-1}F_j)$ and $(F_l'^{-1}F_j')$, where $F_j$ (resp.\ $F_j'$)
  are lifts of $\hat F$ (resp.\ $\hat F'$) on $U_j\in\cU$.
  From $[(F_l^{-1}F_j)]=[(F_l'^{-1}F_j')]$ follows that there exists a
  $0$-cochain $(G_j)_{j\in J}$ of the sheaf $\Lambda(A^0)$ relative to the
  covering $\cU$, such that
  \[
    F_l'^{-1}F_j'=G_lF_l^{-1}F_jG_j^{-1}
    \text{~on~the~arc~} U_j\cap U_l \,,
  \]
  which can be rewritten to
  \[
    F_j'G_jF_j^{-1} = F_l'G_lF_l^{-1}
    \text{~on~the~arc~} U_j\cap U_l \,.
  \]
  If we set $H_j:=F_j'G_{j}F_j^{-1}$ on $U_{j}$, we get
  \begin{itemize}
    \item that $H_j$ is a solution of $[A,A']$ on every $U_j$, i.e.\ it
      satisfies there ${}^{H_j}A=A'$, since
      \begin{align*}
        {}^{H_j}A &= {}^{F_j'G_{j}F_j^{-1}}A
        \\&={}^{F_j'G_{j}}A^0
        & \text{(since $F_j'$ is a lift of $\hat F'$ on $U_j$)}
        \\&={}^{F_j'}A^0
        & \text{(since $G_j$ is a is an isotropy of $A^0$)}
        \\&=A'
        & \text{(since $F_j$ is a lift of $\hat F$ on $U_j$)}
      \end{align*}
      and
    \item which satisfies $\hat F'=\hat H_j\hat F$ on every $U_j$, since
      \begin{align*}
        \hat H_j\hat F&= \widehat{F_j'G_{j}F_j^{-1}} \hat F
        \\&= \hat{F_j'}
        \underset{\id}{%
          \underset{\text{\rotatebox[origin=c]{-90}{$=$}}}{%
            \underbrace{%
              \hat{G_{j}}
            }
          }
        }
        \hat{F_j^{-1}} \hat F
        & \text{(since $G_j$ is flat, i.e.\ $\hat G_j=\id$)}
        \\&= \hat{F'}
        \underset{\id}{%
          \underset{\text{\rotatebox[origin=c]{-90}{$=$}}}{%
            \underbrace{%
              \hat{F^{-1}} \hat F
            }
          }
        }
        \\&= \hat{F'}
      \end{align*}
  \end{itemize}
  Therefore are $(A,\hat F)$ and $(A,\hat F')$ equivalent
  (cf.\ page~\pageref{page:ofDefnOfIsomOfMarkedPairs}) and injectivity is
  proven.
  \iffalse
    \begin{comment}
      \textbf{First look at injectivity:}
      Consider the two elements $(\cM,\nabla,\hat f)$ and
      $(\cM',\nabla',\hat f')$ of $\cH(\cM^{nf},\nabla^{nf})$ which map to same
      cohomology class
      \[
        \exp((\cM,\nabla,\hat f))=\lambda=\exp((\cM',\nabla',\hat f'))
          \in H^1(S^1;\Lambda(A^0)) \,.
      \]
      Since we can use refined coverings, it is possible to find a finite
      covering $\cU=\{U_j;j\in J\}$ of $S^1$ such that $\lambda$ is the class
      of the cocycles $(f_lf_j^{-1})$ and $(f_l',f_j'^{-1})$, where
      $f_j$,$f_j'$ are defined on $U_j$.
      Since $[(f_lf_j^{-1})]=[(f_l'f_j'^{-1})]$ there exists a $0$-cochain
      $(g_j)$ of the sheaf $\Aut^{<0}(\tilde\cM^{nf})$ relative to the covering
      $(I_j)$, such that
      \[
        f_l'f_j'^{-1}=g_lf_lf_j^{-1}g_j^{-1} \text{ on } I_j\cap I_l.
      \]
      If we set $\sigma=f_j^{-1}g_{j}^{-1}f_j'$ on $I_{j}$, we get a horizontal
      section\TODO[~on~???], thus\TODO[why?] it satisfies
      $\sigma\circ\hat{f'}=\hat f$. Therefore are $(\cM,\nabla,\hat f)$ and
      $(\cM',\nabla',\hat{f'})$ isomorphic and injectivity is proven.
    \end{comment}
  \fi
\end{proof}

For the proof of the surjectivity we will use another result from Malgrange and
Sibuya, which is also called the Malgrange-Sibuya Theorem
(Theorem~\ref{thm:thm1helpMalgSibuy}). It can for example be found in Babbitt
and Varadarajans's book \cite[65ff]{babbitt1989local} as Theorem 4.2.1.

Let $\hat F\in G(\!(t)\!)$ be a matrix with formally meromorphic entries. By
the Borel-Ritt Lemma (cf.\ Theorem~\ref{thm:borel-ritt}) we then know, that
there exists for every sector $\mathfrak{s}\subsetneq S^1$ a holomorphic
function $G:\mathfrak{s}\to\GL_n(\C)$ which is asymptotic to $\hat F$.
We will denote the set of all such holomorphic functions, which are on
the arc $I$ asymptotic to $\id\in G(\!(t)\!)$ by
\[
  \cG(I)=\left\{G\in\Gl_n(\cA(I))\mid g\sim_I\id\right\}\,,
\]
and this defines a sheaf $\cG$ on $S^1$.
The statement of the (second) Malgrange-Sibuya Theorem
(Theorem~\ref{thm:thm1helpMalgSibuy}) is then, that the \rewrite{difference}
between formal and konvergent invertible matrices is described by the first
sheaf cohomology $H^1(S^1;\cG)$ of $\cG$ via the map
\[
  \Theta: G(\!(t)\!)/G(\!\{t\}\!)\longrightarrow H^1(S^1;\cG) \,,
\]
which will turn out to be an isomorphism. It is set up as follows:
\begin{einr}
  Let $[\hat F]\in G(\!(t)\!)/G(\!\{t\}\!)$ with ambassador $\hat F$ and
  let $\cU=\{U_j\mid j\in J\}$ be a finite covering of $S^1$ by open arcs.
  The Borel-Ritt Lemma yields for every arc $j\in J\subsetneq S^1$ a
  holomorphic function $F_j$ which satisfies $F_j\sim_{U_j}\hat F$.
  By $(F_lF_j^{-1})_{j,l\in J}$ is then a cocycle for $\cG$ defined,
  and write $\Theta([\hat F])$ for the corresponding cohomology class.
\end{einr}
This construction is similar to the definition of the map of
Theorem~\ref{thm:mainThm1}. The difference is, that we instead of M.A.E.D, to
obtain lifts in the sense of Definition~\ref{defn:lift}, we use only the
Borel-Ritt Lemma to obtain only asymptotic lifts.

It can be verified, that the class $\Theta([\hat F])$ does not depend on
\begin{itemize}
  \item the choise of an ambassador $\hat F$ in
    $[\hat F]\in G(\!(t)\!)/G(\!\{t\}\!)$\PROBLEM[proof!],
  \item the choice of the covering $\cU$\PROBLEM[proof!] nor
  \item the choice the $F_j$\PROBLEM[proof!].
\end{itemize}
\begin{lem}
  \TODO[remove this lemma? is not needed/used]
  The mapping $\Theta$ is injective.
\end{lem}
\begin{proof}
  Let $\hat F$ and $\hat F'\in G(\!(t)\!)$ such that
  $\Theta([\hat F])=\Theta([\hat F'])$.
  We then can find a covering $\cU=\{U_j\mid j\in J\}$ together with
  holomorphic functions $F_j$ and $F_j'$, which satisfy
  $F_j\sim_{U_j}\hat F$ and $F_j'\sim_{U_j}\hat F'$, such that
  $(F_l^{-1}F_j)_{j,l\in J}$ and $(F_l'^{-1}F_j')_{j,l\in J}$ determine the
  classes $\Theta([\hat F])$ and $\Theta([\hat F'])$.
  This implies that there are maps $G_j$, which are on $U_j$ holomorphic and
  satisfy $G_j\sim_{U_j}\id$ such that
  \[
    F_l'^{-1}F_j'=G_lF_l^{-1}F_jG_j^{-1}
    \text{~on~the~arc~} U_j\cap U_l
  \]
  This equation can be rewritten to
  \[
    F_j'G_jF_j^{-1}=F_l'G_lF_l^{-1}
    \text{~on~the~arc~} U_j\cap U_l \,.
  \]
  Since this tells us, that the functions $F_j'G_jF_j^{-1}$ coincide on
  the overlapping and define a holomorphic map from the arc $S^1$ (i.e.\ a
  punctured disc with a small radius) into $\gl_n(\C)$, which will be called
  $G$.
  Since $F_j'G_jF_j^{-1}\sim_{U_j}\id$ for all $j\in J$, we have
  $G\sim\id$.
  \PROBLEM[Riemannscher hebbarkeits satz]
  Thus the defined $G$ satisfies $G=F'^{-1}F$, so that $[F]=[F']$.
\end{proof}
\begin{thm}[Malgrange-Sibuya]\label{thm:thm1helpMalgSibuy}
  The map $\Theta$ is an isomorphism
  \[
    G(\!(t)\!)/G(\!\{t\}\!)\cong H^1(S^1;\cG).
  \]
\end{thm}
This theorem is proven in Section 4.4 of Babbitt and Varadarajan's book
\cite{babbitt1989local} or on page 371 of \cite{Martinet1991}.

We are now able to proof the surjectivity of the map from
Theorem~\ref{thm:mainThm1}.
\begin{proof}[Proof of surjectivity]
  \marginnote{\cite[72]{babbitt1989local}}
  Let the cohomology class $\lambda\in H^1(S^1;\Lambda(A^0))$ be represented by
  a cocycle $(F_{jl})_{j,l\in J}$ associated with some finite covering
  $\cU=\{U_j;j\in J\}$ of $S^1$. We especially know, that
  \begin{itemize}
    \item $F_{jl}$ is on $U_j\cap U_l$ asymptotic to $\id$ and
    \item it is a isotropy, i.e.\  ${}^{F_{jl}}A^0=A^0$.
  \end{itemize}
  The cocycle $(F_{jl})_{j,l\in J}$ also determines an element in
  $\sigma\in H^1(S^1;\cG)$.
  From the Theorem~\ref{thm:thm1helpMalgSibuy} we know, that there is a $\hat
  F\in G\llbracket t\rrbracket\subset G(\!(t)\!)$ whose class $[\hat F]$ gets
  via $\Theta$ mapped to $\sigma$.
  Thus there exists holomorphic functions $F_j:\mathfrak{s}_{U_j}\to\gl_n(\C)$
  with $F_j\sim_{U_j}\hat F$ and $F_l^{-1}F_j=F_{jl}$ on
  $\mathfrak{s}_{U_j\cap U_l}$ for all $j,l\in J$.

  Define on every arc $U_j$ the matrix $A_j:={}^{F_j}A^0$.
  On the intersections $U_j\cap U_l$ we know that $A_j=A_l$, since
  from $F_l^{-1}F_j\in\Lambda(A^0)$ follows on $U_j\cap U_l$ that
  \[
    A^0={}^{F_l^{-1}}({}^{F_j}A^0)
    \qquad\Longrightarrow{}\qquad
    \underset{=A_l}{\underbrace{{}^{F_l}A^0}}
    =\underset{=A_j}{\underbrace{{}^{F_j}A^0}}
    \,.
  \]
  Thus the $A_j$ \rewrite{glue to a} section $A$, which satisfies
  ${}^{\hat F}A=A_0$ by construction.
  We have found an element $(A,\hat F)\in\cH(A^0)$ whose image under $\exp$ is
  $\sigma$.
\end{proof}

\iffalse
\begin{comment}
  \TODO[Define $\tilde\cM$ or find other way!]
  \begin{proof}[Proof of surjectivity]
    \begin{multicols}{2}
      % \textbf{Now look at surjectivity:}
      Similar to the proof, given by Sabbah \marginnote{Which refers to
      \cite{Malgrange1983}} in \cite{sabbah2007isomonodromic}, we will start this
      part of the proof by giving a necessary and sufficient condition for a
      class $\lambda$ in $H^1(S^1;\Lambda(A^0))$
      \TODO[$\Lambda(A^0)\sim\Aut^{<0}(\tilde\cM^{nf})$ or $\Aut^{<0}(\cM^{nf})$?]
      to come from an object
      $(\cM,\nabla,\hat f)\in\cH(\cM^{nf},\nabla^{nf})$:
      \begin{einr}
        This is the case if and only if the image of
        $\lambda\in\Aut^{<0}(\cM^{nf})$ in the set
        $H^1(S^1;\Aut_{\cA}(\tilde\cM^{nf}))$ (where $\Aut_{\cA}(\tilde\cM^{nf})$
        contains only the $\cA$-linear automorphisms) is the identity.
      \end{einr}

    \columnbreak

      \textcolor{gray}{%
        \textbf{Now look at surjectivity:}
        Similar to the proof, given by Sabbah \marginnote{Which refers to
        \cite{Malgrange1983}} in \cite{sabbah2007isomonodromic}, we will start
        this part of the proof by giving a necessary and sufficient condition
        for a class $\lambda$ in $H^1(S^1;\Lambda(A^0))$
        to come from an object
        $(A,\hat F)\in\cH(A^0)$:
        \begin{einr}
          \rewrite{This is the case if and only if the image of
            $\lambda\in\Aut^{<0}(\cM^{nf})$ in the set
            $H^1(S^1;\Aut_{\cA}(\tilde\cM^{nf}))$ (where
            $\Aut_{\cA}(\tilde\cM^{nf})$ contains only the $\cA$-linear
            automorphisms) is the identity.}
        \end{einr}
      }
    \end{multicols}
    \begin{proof}
      \textbf{``\Rightarrow{}'':}
      If $\lambda$ is the image of some $(\cM,\nabla,\hat f)$ then there exists
      \begin{itemize}
        \item a covering $(I_{j})$ of $S^1$ and
        \item isomorphisms $f_j:\tilde\cM\overset{\sim}\to\tilde\cM^{nf}$
          inducing $\hat f$
      \end{itemize}
      such that $\lambda$ comes from a cocycle $(\lambda_{j,l})=(f_lf_j^{-1})$
      on $I_j\cap I_l$.
      \TODO{} shows that $(\lambda_{jl})$ is a coboundary of
      $\Aut_\cA(\tilde\cM^{nf})$.

      \textbf{``\Leftarrow{}'':}
      If for some suitable covering $(I_j)$ the cocycle $(\lambda_{jl})$ is a
      coboundary with values in $\Aut_\cA(\tilde\cM^{nf})$, i.e.\
      $\lambda_{jl}=f_lf_j^{-1}$, we define a new connection $\nabla$ on
      $\tilde\cM^{nf}$ by conjugating $\nabla^{nf}$ by $f_j$ on $U_j$.

      \TODO{}

      Moreover $\hat f_j=\hat f_l$ on $U_j\cap U_l$, so that the formal
      isomorphisms
      \[
        \hat f_j:(\hat \cM^{nf},\nabla)
        \overset{\sim}{\longrightarrow}
        (\hat\cM^{nf},\nabla^{nf})
      \]
      can be glued in an isomorphism $\hat f:(\hat \cM^{nf},\nabla)
      \overset{\sim}{\longrightarrow}(\hat\cM^{nf},\nabla^{nf})$.
    \end{proof}

    Thus, the proof of~\ref{thm:mainThm1} is a consequence of the following
    theorem by Malgrange and Sibuya.
    \begin{thm}[Malgrange-Sibuya]\label{thm:malgSibuyaHelp}
      \marginnote{\cite[Thm.II.6.10]{sabbah2007isomonodromic}}
      The image of the mapping
      \[
        H^1(S^1;\Gl_d^{<0}(\cA_{\tilde D}))
        \to
        H^1(S^1;\Gl_d(\cA_{\tilde D}))
      \]
      is the identity.
    \end{thm}
    For the proof of Theorem~\ref{thm:malgSibuyaHelp} which we refer to
    \cite[Th.A.1]{Malgrange1983}, \cite[Th.6.4.1]{sibuya1990Linear} and
    \cite{babbitt1989local}.
  \end{proof}
\end{comment}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Stokes group}\label{sec:StokesGroup}
\PROBLEM[rewrite!]
Here we want to introduce the notion of Stokes groups. They are for example
also introduced in \cite{Loday1994}, \cite{Loday2014} or section 4
of~\cite{Martinet1991}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Anti-Stokes directions and the Stokes group}
\marginnote{\cite[I.4]{Loday1994}}
Let us recall, that the normal form $A^0$ can be written as
$A^0=Q'(t^{-1})+L\frac{1}{t}$ and a normal solution is given by
$\cY_0(t)=t^Le^{Q(t^{-1})}$ (cf.\ Proposition~\ref{prop:fundSolBuilder}), where
$Q(t^{-1})=\bigoplus_{j\in\{1,\dots,s\}}q_j(t^{-1})\cdot\id_{n_j}$ and the
block structure of $L$ is finer then the structure of $Q$
(cf.\ definition~\ref{defn:structureComparison}).
Let $\left\{q_1(t^{-1}),\dots,q_s(t^{-1})\right\}$ be the \emph{set of all
determining polynomials of $[A^0]$} and denote by
\[
  \cQ(A^0):=\left\{\left(q_j-q_l\right)(t^{-1})
    \mid
    q_j,q_l\in\left\{q_1(t^{-1}),\dots,q_s(t^{-1})\right\},
    q_j \neq q_l
  \right\}
\]
the \emph{set of all determining polynomials of $[\End A^0]$}.
Instead of $q_j-q_l\in\cQ(A^0)$ we will sometimes talk of (ordered) pairs
$(q_j,q_l)\in\cQ(A^0)$.
\begin{defn}\label{defn:determiningPolysOfEndA}
  We call
  \begin{itemize}
    \item $a_{jl}\in\C\backslash\{0\}$ the \emph{leading factor},
    \item $\frac{a_{jl}}{t^{k}}=:q_{jl}(t^{-1})$ the \emph{leading
      coefficient} and
    \item $k_{jl}\in\Q$ the \emph{degree}
  \end{itemize}
  of $q_j-q_l\in\cQ(A^0)$ if
  \[
    q_j-q_l\in\left\{\frac{a_{jl}}{t^{k_{jl}}}+h \mid h \in o(t^{-k_{jl}}),
      a_{jl}\neq0
    \right\}\,.
  \]
  \begin{s-rem}
    \begin{enumerate}
      \item It is obvious that $k_{jl}=k_{lj}$ and
        $q_{jl}(t^{-1})=-q_{lj}(t^{-1})$.
      \item In Boalch's paper \cite{boalch} (and also in \cite{thboalch}) is
        the \rewrite{$k$ always incremented by one}.
        We will prefer the \rewrite{other notion}, which is also used in
        Loday-Richaud's paper \cite{Loday1994}.
      \item In Loday-Richaud's book \cite[Def.4.3.6]{Loday2014} $a_{jl}$ is
        negated to be consistend with calculations at $\infty$.
        Here this is not necessary, since we use the clockwise orientation on
        $S^1$ (cf.\ Definition~\ref{defn:antiStokesDir}).
    \end{enumerate}
  \end{s-rem}
  The degrees of the elements in $\cQ(A^0)$ are defined to be  the
  \emph{levels} of $A^0$.
  The set of all levels of $A^0$ will be denoted by
  \[
    \cK=\{k_1<\dots<k_r\} \subset \Q \,.
  \]
  \begin{s-rem}
    The system $[A^0]$ is unramified if and only if $\cK\subset\Z$.
    Since we only want to consider the unramified case, this will be always the
    case.
  \end{s-rem}
\end{defn}

\begin{defn}
  \marginnote{\cite[130]{hotta2008}, \cite[79]{Loday2014}}
  Let $k\in\N$ and $a\in\C$.
  An exponential $e^{q(t^{-1})}$, where $q(t^{-1})=\frac{a}{t^{k}}+o(t^{-k})$,
  has \emph{maximal decay in a direction $\theta\in S^1$} if and only if
  $ae^{-ik\tilde\theta}$ is real negative.
\end{defn}

On the determining polynomials of $[A^0]$ we define the following (partial)
order relations:
\begin{defn}\label{defn:definingRelations}
  Let $\tilde\theta$ be a determination of $\theta$.
  \begin{itemize}
    \item We define the relation
      $\boldmath q_j \underset{\tilde\theta}{\prec} q_l$ to be equivalent to
      the condition
      \begin{einr}
        $e^{(q_j-g_l)(t^{-1})}$ is flat at $0$ in a neighbourhood of the
        direction $\tilde\theta$.
      \end{einr}
    \item Let us define another relation
      $\boldmath q_j \underset{\tilde\theta,\max}{\prec} q_l$ equivalent to
      \begin{einr}
        $e^{(q_j-g_l)(t^{-1})}$ is of maximal decay in the direction
        $\tilde\theta$.
      \end{einr}
  \end{itemize}
  \begin{s-rem}
    In the unramified case do these relations not depend on the determination
    $\tilde\theta$ of $\theta$. As a consequence we will only write
    $\underset{\theta}{\prec}$ and $\underset{\theta,\max}{\prec}$.
  \end{s-rem}
\end{defn}
We know that
\begin{enumerate}
  \item the condition $q_j \underset{\theta}{\prec} q_l$ is
    satisfied if and only if $\Re(a_{jl}e^{-ik_{jl}\theta})<0$ and
  \item the condition $q_j \underset{\theta,\max}{\prec} q_l$ is
    equivalent to
    \begin{einr}
      $a_{jl}e^{-ik_{jl}\theta}$ is a real negative
      number, i.e.\ $q_j \underset{\theta}{\prec} q_l$ and
      $\Im(a_{jl}e^{-ik_{jl}\theta})=0$.
    \end{einr}
\end{enumerate}
Thus it is convenient to look closer at functions of the form
$f:\theta\mapsto ae^{-ik\theta}$, corresponding to some pair $(q_j,q_l)$.
Write $a$ as $a=|a|e^{i\arg(a)}$, thus the function writes as
\begin{align*}
  f(\theta)&=|a|e^{i(\arg(a)-k\theta)}
  \\&=|a|(\cos(\arg(a)-k\theta) + i\sin(\arg(a)-k\theta)) \,.
\end{align*}
In the figure~\ref{fig:functionF}, we illustrate the real and the imaginary
part of $f$.
\begin{figure}[h!] %{{{
  \begin{flushright}
    \tikzmarkc{n2}{purple} here is $\Im(ae^{-ik\theta})=0$
  \end{flushright}
  \begin{center}
    \begin{tikzpicture}[scale=4]
      \pgfmathsetmacro{\k}{3}
      \pgfmathsetmacro{\argA}{0.3}
      \pgfmathsetmacro{\absA}{0.4}

      \begin{scope}[thick]
        \clip (-0.6,{\absA+0.1}) rectangle (2.6,{-\absA-0.1});
        \foreach \x in {-2,-1,...,3}{
          \pgfmathsetmacro{\s}{{\argA + \x / \k * 2 - 1/2/\k}};
          \fill[blue!10!white]
            ({\s + 2/2/\k},0) sin ({\s + 3/2/\k},{-\absA})
                              cos ({\s + 4/2/\k},0);
          \draw[blue!40!black] (\s,0) sin ({\s + 1/2/\k},\absA)
                       cos ({\s + 2/2/\k},0)
                       sin ({\s + 3/2/\k},{-\absA})
                       cos ({\s + 4/2/\k},0);
          \fill[white] ({\s + 3/2/\k},{-\absA}) circle (1pt);
          \fill[blue!40!black] ({\s + 3/2/\k},{-\absA}) circle (.4pt);
          \pgfmathsetmacro{\s}{{\argA + \x / \k * 2}};
          \draw[purple] (\s,0) sin ({\s + 1/2/\k},\absA)
                       cos ({\s + 2/2/\k},0)
                       sin ({\s + 3/2/\k},{-\absA})
                       cos ({\s + 4/2/\k},0);
          \fill[white] (\s,0) circle (1pt);
          \fill[purple] (\s,0) circle (.4pt);
          \fill[white] ({\s + 2/2/\k},0) circle (1pt);
          \fill[purple] ({\s + 2/2/\k},0) circle (.4pt);
        }
      \end{scope}
      \draw [blue!40!black,dashed]
        ({\argA+4/\k + 1/2/\k},{-\absA}) -- ({\argA+4/\k + 1/2/\k},0);
      \draw [blue!40!black,dashed]
        ({\argA+4/\k + 3/2/\k},{-\absA}) -- ({\argA+4/\k + 3/2/\k},0);
      \draw [blue!40!black, thick
            ,decorate
            ,decoration={brace,mirror,amplitude=10pt}
            ,xshift=0pt
            ,yshift=0pt]
        ({\argA+4/\k + 1/2/\k},{-\absA}) -- ({\argA+4/\k + 3/2/\k},{-\absA})
        node [midway,yshift=-7pt] {$\tikzmark{g0}$};

      \node at ({\argA+2 - 3/\k},0) {$\tikzmark{f-1}$};
      \node at ({\argA+2 - 2/\k},0) {$\tikzmark{f0}$};
      \node at ({\argA+2 - 1/\k},0) {$\tikzmark{f1}$};

      \node at ({\argA-2/\k + 2/2/\k},{-\absA}) {$\tikzmark{e-1}$};
      \node at ({\argA + 2/2/\k},{-\absA}) {$\tikzmark{e0}$};
      \node at ({\argA+2/\k + 2/2/\k},{-\absA}) {$\tikzmark{e1}$};
      \node at ({\argA+4/\k + 2/2/\k},{-\absA}) {$\tikzmark{e2}$};

      \draw (-0.6,0) -- (2.6,0);
      \draw[dotted] (-0.6,\absA)node[left,font=\tiny] {$|a|$} -- (2.6,\absA);
      \draw[dotted] (-0.6,{-\absA})node[left,font=\tiny] {$-|a|$} -- (2.6,{-\absA});
      \foreach \x in {-0.5,0,...,2.5}{
        \draw[dotted] ({\x},{-\absA}) -- ({\x},{\absA + 0.1})
          node [above,font=\tiny,] {\x \pi};
      }
      \draw[thick, dotted, green!50!black] (\argA,{-\absA}) -- (\argA,{\absA + 0.1})
        node [above,font=\tiny,] {$\frac{\arg(a)}{k}$};
    \end{tikzpicture}
  \end{center}
  \begin{flushright}
    \tikzmarkc{n3}{blue} here is $q_j \underset{\theta}{\prec} q_l$
  \end{flushright}
  \begin{flushright}
    \tikzmarkc{n1}{blue} here is $q_j \underset{\theta,\max}{\prec} q_l$
  \end{flushright}
  \begin{tikzpicture}[remember picture,overlay]
    \draw[->,blue!50!white,thick] (n3) to[out=150,in=270] (g0);
    \draw[->,purple!50!white,thick] (n2) to[out=240,in=70] (f-1);
    \draw[->,purple!50!white,thick] (n2) to[out=265,in=120] (f0);
    \draw[->,purple!50!white,thick] (n2) to[out=290,in=70] (f1);
    \draw[->,blue!50!white,thick] (n1) to[out=180,in=270] (e-1);
    \draw[->,blue!50!white,thick] (n1) to[out=170,in=270] (e0);
    \draw[->,blue!50!white,thick] (n1) to[out=160,in=270] (e1);
    % \draw[->,blue!40!black,thick] (n1) to[out=150,in=270] (e2);
  \end{tikzpicture}
  \caption{In this plot is the real part of $f(\theta)=ae^{-ik\theta}$,
    corresponding to some pair $(q_j,q_l)$, in
    \textcolor{blue!60!white}{blue} and the imaginary part in
    \textcolor{purple}{purple} sketched.
  }\label{fig:functionF}
\end{figure} %}}}

The graphs, corresponding to the flipped pair $(q_l,q_j)$ are then obtained by
the transformation $\arg(a)\to\arg(-a)=\arg(a)+\pi$, i.e.\ the shift by
$\frac{\pi}{k}$ to the right. This $\frac{\pi}{k}$ is exactly a half period,
thus the new graphs are obtained by \rewrite{mirroring at the line $t=0$.}
\begin{rem}\label{rem:relationDistanceCondition}
  Let $k_{jl}$ be the degree of $q_j-q_l$.
  It is easy to see (cf.\ Figure~\ref{fig:functionF}), that the condition
  \[
    q_j \underset{\theta}{\prec} q_l
  \]
  is equivalent to
  \begin{einr}
    there is a $\theta'\in U(\theta,\frac{\pi}{k_{jl}})$ such that
    $q_j \underset{\theta,\max}{\prec} q_l$.
  \end{einr}
\end{rem}

\begin{defn}\label{defn:antiStokesDir}
  % \marginnote{See \cite[Def.I.4.5]{Loday1994}(for the ramified case)
  %   \cite[Def.3.2]{boalch}}
  \begin{enumerate}
    \item $\alpha$ is an \emph{anti-Stokes direction} if there is at least one
      pair $(q_j,q_l)$ in $\cQ(A^0)$, which satisfies
      $q_j \underset{\alpha,\max}{\prec} q_l$.
      \begin{itemize}
        \item Let $\A=\{\alpha_1,\dots,\alpha_{\nu}\}$ denote the set of all
          anti-Stokes directions in a clockwise ordering. For a uniform
          notation later, \rewrite{define $\A$ to contain a single, arbitrary
          direction if $\cK=\{0\}$.}
          \TODO[Is this used somewhere??]
          \begin{s-rem}
            The clockwise ordering is chosen, similar to Loday-Richaud's paper
            \cite{Loday1994}, since the calculations are then compatible with
            the calculations, which look at $\infty$ and take a
            counterclockwise ordering.
            Boalch uses in \cite{boalch} and \cite{thboalch} the inverse
            ordering, but looks also at $0$, thus there might be some
            incompatibilities.
            In Loday-Richaud's book \cite{Loday2014} this problem is solved by
            an additional minus sign for some koefficients\comm{~to $a_{ij}$}.
            \PROBLEM[mentioned to often?]
          \end{s-rem}
      \end{itemize}
    \item $\theta$ is a \emph{Stokes direction} if there is at least one pair
      $(q_j,q_l)$ in $\cQ(A^0)$, which satisfies neither
      $q_j\underset{\theta}{\prec} q_l$ nor $q_l\underset{\theta}{\prec} q_j$.
      \begin{itemize}
        \item Let $\S=\{\sigma_1<\cdots<\sigma_\mu\}$ be the set of Stokes
          directions.
      \end{itemize}
  \end{enumerate}
\end{defn}
We will use the greek letter $\alpha$ when we want to emphasize that a
direction is an anti-Stokes direction.
For generic directions, we will use $\theta$.
In fact will most of the following definitions and
constructions work for every $\theta\in S^1$, but the Stokes group
(cf.\ Definition~\ref{defn:stokesGroup}) for example will be trivial
for every $\theta\notin\A$.
Thus the interesting directions are  only the anti-Stokes directions
$\alpha\in\A$.

\begin{lem}\label{lem:rotationalSym}%\label{rem:rotationalSymPrime}
  If $\alpha\in\A$ together with a determining pair
  $(q_j-q_l)(t^{-1})\in\cQ(A^0)$ of degree $k_{jl}$ is given, we have for every
  $m\in\N$ that
  \[
    \underset{=:\alpha'}{\underbrace{\alpha+m\frac{\pi}{k_{jl}}}} \in \A \,.
  \]
  Especially is either $q_j \underset{\alpha',\max}{\prec} q_l$ (in the
  case, when $m$ is even) or $q_l \underset{\alpha',\max}{\prec} q_j$
  (when $m$ is uneven) satisfied (see figure~\ref{fig:functionF}).
  \begin{s-cor}
    It follows that in the case $\cK=\{k\}$, the set $\A$ has
    $\frac{\pi}{k}$-rotational symmetry.
  \end{s-cor}
\end{lem}
\begin{proof}
  \marginnote{\cite[8]{thboalch}}
  Let $(j,l)$ be a pair such that
  $q_j \underset{\alpha,\max}{\prec} q_l$, i.e.\ such that
  $a_{jl}e^{-ik_{jl}\alpha}\in\R_{<0}$.
  Hence, for $m\in\N$,
  \begin{align*}
    a_{jl}e^{-ik_{jl}\left(\alpha+m\frac{\pi}{k_{jl}}\right)}
    &=a_{jl}e^{-ik_{jl}\alpha}e^{-im\pi}
    = \begin{cases}
      a_{jl}e^{-ik_{jl}\alpha}\in\R_{<0}
        & \text{, if $m$ is even}
    \\-a_{jl}e^{-ik_{jl}\alpha}\in\R_{>0}
        & \text{, if $m$ is uneven}
    \end{cases}
  \end{align*}
  is, in the case when $m$ is even, also real and negative. In the other
  case, when $n$ is uneven, we use that $a_{jl}=-a_{lj}$ and $k_{jl}=k_{lj}$ to
  obtain
  $a_{lj}e^{-ik_{lj}\left(\alpha+m\frac{\pi}{k_{lj}}\right)} \in\R_{<0}$.

  Thus, for $\alpha':=\alpha+m\frac{\pi}{k_{jl}}$, we have $\alpha'\in\A$ since
  \begin{itemize}
    \item $q_j \underset{\alpha',\max}{\prec} q_l$ when $m$ is even or
    \item $q_l \underset{\alpha',\max}{\prec} q_j$ when $m$ is uneven.
  \end{itemize}
\end{proof}

As a \rewrite{subgroup of the stalk at $\theta$} of the in
Definition~\ref{defn:StokesSheaf} defined Stokes sheaf $\Lambda(A^0)$ we
define the Stokes group as follows.
\begin{defn}\label{defn:stokesGroup}
  Define the \emph{Stokes group}
  \[
    \Sto_\theta(A^0):=
    \left\{\phi_\theta\in\Lambda_\theta(A^0)
      \mid \phi_\theta \text{~has maximal decay at~} \theta
    \right\}
  \]
  whose elements are called \emph{Stokes germs}.
  \TODO[This is in fact a group, since\dots]
  \begin{s-rem}
    For $\theta\notin\A$ the group $\Sto_\theta(A^0)$ is trivial, since no flat
    isotropy has maximal decay, but the identity.

  \end{s-rem}
\end{defn}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stokes matrices}\label{sec:matrixReps}
\marginnote{\cite[9f]{thboalch}, \cite[??]{Loday1994}}
\begin{defn}\label{defn:groupOfFaithfullReps}
  Let us use
  \[
    \bdelta_{jl}:=
    \begin{cases}
      0 \in \C^{n_j\times n_l} & \text{,~if~} j\neq l
    \\\id \in \C^{n_j\times n_l} & \text{,~if~} j=l
    \end{cases}
  \]
  as a block version of Kronecker's delta.
  Define the group
  \begin{align*}
    \SSto_\theta(A^0)= \Big\{K=(K_{jl})_{j,l\in\{1,\dots,s\}}\in\GL_n(\C) \mid
      K_{jl}=\bdelta_{jl} \text{~unless~}
      q_j \underset{\theta,\max}{\prec} q_l \Big\}
  \end{align*}
  of all \emph{Stokes matrices} of $A^0$ in the direction $\theta$.
  They will arise as a faithful representation
  (cf.\ Section~\ref{sec:faithRepre}) of $\Sto_\theta(A^0)$.
  \begin{s-rem}
    In Boalch's publications \cite{boalch,thboalch} are our Stokes matrices
    called Stokes factors, since he introduces other objects, he wants to call
    Stokes matrices.
  \end{s-rem}
\iffalse
  % \begin{s-rem}
  %   \BIGPROBLEM[needs more assumptions!]
  %   \begin{comment}
  %     Loday-Richaud defines Stokes matrices in \cite[Defn.III.3.4]{Loday1994}.
  %   \end{comment}
  %   Let
  %   \begin{itemize}
  %     \item $q_1 = \frac{2}{t^k} + \frac{2}{t^{k-1}}$,
  %     \item $q_2 = \frac{1}{t^k} + \frac{1}{t^{k-1}}$ and
  %     \item $q_3 = \frac{2}{t^k} + \frac{1}{t^{k-1}}$
  %   \end{itemize}
  %   be the three diagonal elements of $Q$ of some system $A$.
  %   Thus the determining polynomials are given by
  %   \begin{itemize}
  %     \item $q_{1,2}=q_1-q_2 = \frac{1}{t^k}$,
  %     \item $q_{1,3}=q_1-q_3 = \frac{1}{t^{k-1}}$ and
  %     \item $q_{3,2}=q_3-q_2 = \frac{1}{t^k}$.
  %   \end{itemize}
  %   Since the leading terms of $q_{1,2}$ and $q_{3,2}$ are equal, they
  %   determine the same anti-Stokes directions. Let $\theta$ be one of these
  %   directions, which satisfies neither
  %   $q_1\underset{\theta,\max}{\prec}q_3$ nor
  %   $q_3\underset{\theta,\max}{\prec}q_1$ (it is always possible, to find such
  %   a direction since the level of $q_{1,3}$ is different to the levels of the
  %   other ones).
  %   The group of Stokes matrices at $\theta$ is then given by
  %   \[
  %     \SSto_\theta(A^0)=\left\{
  %       K= \begin{pmatrix}
  %         1 & a & 0
  %       \\0 & 1 & 0
  %       \\0 & b  & 1
  %       \end{pmatrix}
  %       \mid
  %       a,b \in\C
  %     \right\}
  %   \]
  %   But $\SSto_\theta(A^0)$ is \textbf{not closed under the product}, i.e.\
  %   \[
  %     \begin{pmatrix}
  %       1 & a & 0
  %     \\0 & 1 & 0
  %     \\0 & 0 & 1
  %     \end{pmatrix}
  %     \begin{pmatrix}
  %       1 & 0 & 0
  %     \\0 & 1 & b
  %     \\0 & 0 & 1
  %     \end{pmatrix}
  %     =
  %     \begin{pmatrix}
  %       1 & a & \textcolor{red!60!black}{ab}
  %     \\0 & 1 & b
  %     \\0 & 0 & 1
  %     \end{pmatrix}
  %     \notin \SSto_\theta(A^0)
  %     \,.
  %   \]
  %   \textcolor{green!40!black}{Maybe define the Stokes matrices as:}
  %   \[
  %     \SSto_\theta(A^0)=\left\{
  %       K= \begin{pmatrix}
  %         1 & a & ab
  %       \\0 & 1 & b
  %       \\0 & 0 & 1
  %       \end{pmatrix}
  %       \mid
  %       a,b \in\C
  %     \right\}
  %   \]
  % \end{s-rem}
\fi
\end{defn}
Let $\cY_0=t^L e^{Q(t^{-1})}$ be a normal solution corresponding to
$A^0$ (cf.\ Definition~\ref{defn:normSol}).

\begin{prop}\label{prop:representation}
  \marginnote{\cite[Def.I.4.7]{Loday1994}\\\cite[78f]{Loday2014}}
  In this situation is the morphism
  \begin{align*}
    \rho_{\theta}:\Sto_\theta(A^0)&\longrightarrow\SSto_\theta(A^0)
    \\\phi_\theta
    &\longmapsto
    C_{\phi_\theta}:=\cY_{0}^{-1}\phi_\theta\cY_{0}
  \end{align*}
  an isomorphism which maps a germ of $\Sto_\theta(A^0)$ to the corresponding
  Stokes matrix $C_{\phi_\theta}$ such that
  \begin{equation} \label{eq:representation}
    \phi_\theta(t)\cY_{0}(t)
    =\cY_{0}(t)C_{\phi_\theta}
  \end{equation}
  near $\theta$.
  The matrix $C_{\phi_\theta}$ is then called a \emph{representation of
  $\phi_\theta$}.
  \begin{s-rem}
    \begin{enumerate}
      \item In the unramified case does this morphism depend on the choice of
        the determination $\tilde\theta$ of $\theta$ and the corresponding
        choice of a realization of the fundamental solution with that
        determination of the argument near the direction $\theta$
        (cf.~\cite{Loday1994} or~\cite[78f]{Loday2014}).
        \TODO[Satz zu lang]
      \item \marginnote{\cite[Defn.I.4.7]{Loday1994}}
        This construction defines also a morphism, which takes a germ
        $\phi_\theta\in\Lambda_\theta(A^0)\supset\Sto_\theta(A^0)$ into its
        unique representation matrix
        \[
          C_{\phi_\theta} \in
          \underset{\SSto_\theta(A^0)}{%
            \underset{\text{\rotatebox[origin=c]{90}{$\subset$}}}{%
              \hat\SSto_{\theta}(A^0)}}
          :=
          \left\{(K_{jl})_{j,l\in\{1,\dots,s\}}
            \in \GL_n(\C)\mid K_{jl}=\bdelta_{jl} \text{ unless }
            q_j \underset{\theta}{\prec} q_l \right\}
          \,.
        \]
        \begin{comment}
          Does this define a local-constant sheaf
          \[
            I\mapsto \hat\SSto_{I}(A^0)
            :=
            \left\{(K_{jl})_{j,l\in\{1,\dots,s\}}
              \in \GL_n(\C)\mid K_{jl}=\bdelta_{jl} \text{ unless }
              q_j \underset{\theta}{\prec} q_l
              \text{ for some } \theta\in I\right\}
          \]
          and a skyscreaper sheaf
          \[
            I\mapsto \SSto_{I}(A^0) \,.
          \]
          \PROBLEM
        \end{comment}
    \end{enumerate}
  \end{s-rem}
\end{prop}
\begin{proof}
  It is well known (cf.\ \cite[10]{thboalch}), that the morphism
  $\rho_{\theta}$, i.e.\ conjugation by the fundamental solution, relates
  solutions $\phi_\theta$ of $[\End(A^0)]=[A^0,A^0]$ to solutions of $[0,0]$
  which are the constant matrices $\GL_n(\C)$.
  Thus we have to show, that the image of $\Sto_\theta(A^0)$ under
  $\rho_{\theta}$ is $\SSto_\theta(A^0)$.

  To see that the obtained matrix has the necessary zeros, to lie in
  $\SSto_{\theta}(A^0)$ we look at equation (\ref{eq:representation}) and
  deduce
  \begin{equation}\label{eq:repProof1}
    \phi_\theta(t)
    =t^L e^{Q(t^{-1})}C_{\phi_\theta}e^{-Q(t^{-1})}t^{-L}
  \end{equation}
  with the given choice of the argument near $\theta$.
  After decomposing $C_{\phi_\theta}$ into
  \begin{align*}
    C_{\phi_\theta}&=1_n+\begin{pmatrix}
      c_{(1,1)} & c_{(1,2)} & \cdots &\\
      c_{(2,1} & \ddots\\
      \vdots \\
      & & & c_{(s,s)}
    \end{pmatrix}
  \\&=1_n+
    \underset{C_{\phi_\theta}^{(1,1)}}{\underbrace{%
      \begin{pmatrix}
        c_{(1,1)} & 0 & \cdots &\\
        0\\
        \vdots&\\
        &
      \end{pmatrix}
    }}
    +
    \underset{C_{\phi_\theta}^{(1,2)}}{\underbrace{%
      \begin{pmatrix}
        0 & c_{(1,2)} & 0 & \cdots\\
        & 0 &\\
        &\vdots\\
        &
      \end{pmatrix}
    }}
    +\cdots+
    \underset{C_{\phi_\theta}^{(s,s)}}{\underbrace{%
      \begin{pmatrix}
        &\\
        & & & \vdots\\
        & & & 0\\
        & \cdots & 0 & c_{(s,s)}
      \end{pmatrix}
    }}
  \\&=1_n+\sum_{(l,j)}C_{\phi_\theta}^{(l,j)}
  \end{align*}
  where the $c_{(j,l)}$ are blocks\marginnote{One can ignore the block
  structure by using $1\times1$ sized blocks. But one looses the uniqueness of
  the $q_j$'s.} of size $n_j\times n_l$ which correspond to the structure of
  $Q$. After rewriting the Equation (\ref{eq:repProof1}) we get
  \[
    \phi_\theta=
      t^L\left(
        1_n+\sum_{(l,j)}C_{\phi_\theta}^{(l,j)}e^{(q_l-q_j)(t^{-1})}
      \right)t^{-L} \,.
  \]
  \begin{comment}
    \begin{align*}
      \phi_\theta(t)
      &=t^Le^{Q(t^{-1})}\left(
        1_n+C_{\phi_\theta}
      \right)e^{-Q(t^{-1})}t^{-L}
    \\&=t^Le^{Q(t^{-1})}\left(
        1_n+\sum_{(l,j)}C_{\phi_\theta}^{(l,j)}
      \right)e^{-Q(t^{-1})}t^{-L}
    \\&=t^L\left(
        1_n+\sum_{(l,j)}e^{Q(t^{-1})}C_{\phi_\theta}^{(l,j)}e^{-Q(t^{-1})}
      \right)t^{-L}
    \\&=t^L\left(
          1_n+\sum_{(l,j)}C_{\phi_\theta}^{(l,j)}e^{(q_l-q_j)(t^{-1})}
        \right)t^{-L} \,.
    \end{align*}
  \end{comment}
  Thus, for $\phi_{\theta}$ to be flat in direction $\theta$, it is
  necessary and sufficient that if $e^{(q_l-q_j)(t^{-1})}$ does not have
  maximal decay in direction $\theta$ the corresponding
  block $C_{\phi_\theta}^{(l,j)}$ vanishes.
  Thus we have seen, that $C_{\phi_\theta}$ is an
  element of $\SSto_\theta(A^0)$.

  The map $\rho_{\tilde\theta}$ is \textbf{injective}, and thus a faithful
  representation, since conjugation by an invertible matrix defines an
  isomorphism to its \rewrite{image}.

  The \textbf{surjectivity} can also \rewrite{be seen easily}, since every
  constant (unipotent) matrix, with zeros at the necessary positions,
  characterizes a unique element of $\Sto_\theta(A^0)$.
  \TODO[Isomorphic to $\C^{?}$?]
\end{proof}

In particular, from the proof, we get that
\begin{enumerate}
  \item for $j=l$ the (diagonal) blocks $C_{\phi_\theta}^{(l,j)}$ vanish since
    $q_l-q_j=0$ does not have maximal decay and
  \item if $e^{q_j-q_l}$ has has maximal decay, then $e^{q_l-q_j}$ has not.
    Thus if $C_{\phi_\theta}^{(l,j)}$ is not equal to zero, the block
    $C_{\phi_\theta}^{(j,l)}$ is necessarily zero.
\end{enumerate}
\begin{comment}
  \begin{rem}
    This implies that the matrix $C_{\phi_\theta}$ is unipotent, and
    \rewrite{hence is $\Sto_\theta(A^0)$ is a unipotent Lie group.}
  \end{rem}
\end{comment}

\begin{cor}
  \marginnote{\cite[Def.I.4.12]{Loday1994}}
  A germ $\phi_\theta\in\Lambda_\theta(A^0)$ is a Stokes germ, i.e.\ an element
  in $\Sto_\theta(A^0)$, if and only if it has a representation
  $C_{\phi_\theta}$ where
  \[
    C_{\phi_\theta}=1_n +
    \sum_{(l,j)\mid q_j\underset{\theta,\max}{\prec}q_l}
    C_{\phi_\theta}^{(l,j)}
  \]
  and the $C_{\phi_\theta}^{(l,j)}$ have the necessary block structure.

  In other words:
  \begin{einr}
    a germ $\phi_\theta\in\Lambda_\theta(A^0)$ is in $\Sto_\theta(A^0)$ if and
    only if there exists a $C\in\SSto_\theta(A^0)$ such that
    $\phi_\theta=\cY_{0}C\cY_{0}^{-1}$.
  \end{einr}
  \begin{s-rem}
    In Loday-Richaud's book \cite[78]{Loday2014} are the elements of
    $\Sto_\theta(A^0)$ actually characterized as the flat transformations, such
    that equation (\ref{eq:representation}) is satisfied for some unique
    constant invertible matrix $C\in\SSto_\theta(A^0)$.
  \end{s-rem}
\end{cor}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Filtration of the Stokes group by levels}
\marginnote{\cite{Loday1994}, \cite[362ff]{Martinet1991}}
Let us introduce a couple of notations and definitions, which coincide with the
notations used in Loday-Richaud's paper \cite{Loday1994}.
Another good resource is for example the paper~\cite[362f]{Martinet1991} from
Martinet and Ramis.

\begin{defn}
  We denote the set of \emph{levels of the germ}
  $\phi_{\theta}\in\Lambda_\theta(A^0)$ by
  \[
    \cK(\phi_\theta):= \left\{\deg(q_j-q_l)\mid C_{\phi_\theta}^{(l,j)}\neq0
      \text{ in some representation of }\phi_\theta\right\} \subset \cK \,.
  \]
  A germ $\phi_\theta$ is called a \emph{$k$-germ} when
  $\cK(\phi_{\theta})\subset\{k\}$, i.e.\ it has at most the level $k$.
\end{defn}
\begin{notations}
  \marginnote{\cite[Not.I.4.15]{Loday1994},\\\cite[362]{Martinet1991}}
  For $k\in\cK$ and $\theta\in S^1$ we set:
  \begin{itemize}
    \item $\Lambda^{k}(A^0):=$ the subsheaf of $\Lambda(A^0)$ of all germs,
      which are generated by $k$-germs;
    \item $\Lambda^{\leq k}(A^0)$ (resp. $\Lambda^{<k}(A^0)$ or
      $\Lambda^{\geq k}(A^0)$) as the subsheaf of $\Lambda(A^0)$ generated by
      $k'$-germs for all $k'\leq k$ (resp. $k'<k$ or $k'\geq k$);
  \end{itemize}
  The restriction to $\Sto_\theta$ yields the groups
  \[
    \Sto_\theta^\star(A^0):=\Sto_\theta(A^0)\cap\Lambda_\theta^{\star}(A^0)
  \]
  for $\star\in\{k,<k,\leq k,\dots\}$.
  % \begin{itemize}
  %   \item $\Sto_\theta^k(A^0):=\Sto_\theta(A^0)\cap\Lambda_\theta^{k}(A^0)$;
  %   \item $\Sto_\theta^{\leq k}(A^0):=\Sto_\theta(A^0)\cap\Lambda_\theta^{\leq k}(A^0)$;
  %   \item $\Sto_\theta^{<k}(A^0):=\Sto_\theta(A^0)\cap\Lambda_\theta^{<k}(A^0)$;
  % \end{itemize}
  We define also
  \begin{itemize}
    \item $\SSto^\star_\theta(A^0)$ as the groups of representations, which
      correspond to elements of  $\Sto^\star_\theta(A^0)$;
    \item $\A^k:=\left\{\alpha\in\A\mid\Sto_\alpha^k(A^0)\neq\{\id\}\right\}$
      as the set of anti-Stokes directions \emph{bearing the level $k$};
    \item $\A^{\leq k}:=\underset{k'\leq k}\bigcup\A^{k'}$ (resp.
      $\A^{<k}:=\underset{k'<k}\bigcup\A^{k'}$ and
      $\A^{\geq k}:=\underset{k'\geq k}\bigcup\A^{k'}$);
      \begin{s-rem}
        It is clear that
        \begin{itemize}
          \item $\A^{\star}=\left\{\alpha\in\A
            \mid\Sto_{\alpha}^\star(A^0)\neq\{\id\}\right\}$ and
          \item we have the canonical inclusions
            $\A^k\hookrightarrow\A^{\leq k}$ and
            $\A^{<k}\hookrightarrow\A^{\leq k}$.
        \end{itemize}
      \end{s-rem}
    \item $\cK_\alpha:=\left\{k\in\cK\mid\Sto_\alpha^k(A^0)\neq\{\id\}\right\}$
      the set of levels \emph{beared by $\alpha\in\A$}, and
      $K_\alpha=\max\cK_\alpha$ the \emph{maximal level beared by $\alpha$}.
      \begin{s-rem}
        The Lemma~\ref{lem:rotationalSym} implies that from $k\in\cK_{\alpha}$
        follows that $k\in\cK_{\alpha+m\frac{\pi}{k}}$ for $m\in\N$.
      \end{s-rem}
  \end{itemize}
\end{notations}

\begin{comment}
  See \cite[I.5]{Loday1994} on p.\ 861f (See [LR91])
\end{comment}
\rewrite{We will now introduce a filtration of $\Lambda(A^0)$, wich will be
restricted to $\Sto_\theta(A^0)$ and defines there a filtration. This leads to
a decomposition of $\Sto_\theta(A^0)$ into a semidirect product.} Let us start
by studying the sheaves $\Lambda^\star(A^0)$, and discuss how they correlate.

The following proposition can be found as~\cite[Prop.I.5.1]{Loday1994} and the
key-statement is also given in~\cite[Prop.4.10]{Martinet1991}.
\begin{prop}\label{prop:PropertiesOfStokesSheafSplitting}
  \marginnote{\cite[Prop.I.5.1]{Loday1994}}
  For any level $k\in\cK$ one has
  \begin{enumerate}
    \item $\Lambda^{k}(A^0)$, $\Lambda^{\leq k}(A^0)$ and $\Lambda^{<k}(A^0)$
      are sheaves of subgroups of $\Lambda(A^0)$;
    \item the sheaf $\Lambda^k(A^0)$ is normal in $\Lambda^{\leq k}(A^0)$;
      \begin{comment}
        A subgroup $N$ is normal in $G$ ($N\vartriangleleft G$) if it is stable
        under conjugation, i.e.
        \[
          N\vartriangleleft G \Leftrightarrow \forall n\in N \forall g\in G,
          gng^{-1}\in N ,.
        \]
      \end{comment}
    \item \marginnote{\cite[Proposition 10]{Martinet1991}}
      the exact sequence of sheaves
      \[
        1\longrightarrow\Lambda^k(A^0)
        \overset{i}\longrightarrow\Lambda^{\leq k}(A^0)
        \overset{p}\longrightarrow\Lambda^{<k}(A^0)
        \longrightarrow 1 \,,
      \]
      where
      \begin{itemize}
        \item $i:\Lambda^k(A^0)\hookrightarrow\Lambda^{\leq k}(A^0)$ is the
          canonical inclusion and
        \item $p$ is the truncation to terms of levels $<k'$,
      \end{itemize}
      splits.
  \end{enumerate}
\end{prop}
From the splitting of the sequence, we obtain immediately the following
decomposition into a semidirect product.
\begin{cor}\label{cor:factorStokesGerms}
  \marginnote{\cite[Cor.I.5.2]{Loday1994}}
  \begin{enumerate}
    \item For any $k\in\cK$, there are the two following ways of factoring
      $\Lambda^{\leq k}(A^0)$ in a semidirect product:
      \begin{align*}
        \Lambda^{\leq k}(A^0)&\cong \Lambda^{<k}(A^0)\ltimes\Lambda^{k}(A^0)
      \\                     &\cong \Lambda^{k}(A^0)\ltimes\Lambda^{<k}(A^0)\,.
      \end{align*}
      Thus any germ $f^{\leq k}\in\Lambda^{\leq k}(A^0)$ can be uniquely
      written as
      \begin{itemize}
        \item $f^{\leq k}=f^{<k}g^k$, where $f^{<k}\in\Lambda^{<k}$ and
          $g^k\in\Lambda^k$, or
        \item $f^{\leq k}=f^kf^{<k}$, where $f^k\in\Lambda^k$ and
          $f^{<k}\in\Lambda^{<k}$.
      \end{itemize}
      \begin{s-rem}\label{rem:algFactorization}
        \marginnote{\cite[Cor.I.5.2(ii)]{Loday1994}}
        We can get the factor $f^{<k}$ common to both factorizations by
        truncation of $f^{\leq k}$ to terms of level $k$.
        This truncation can explicitly be achieved, in terms of Stokes
        matrices, by keeping in any representation
        $1+\sum C^{(j,l)}$ of $f^{\leq k}$ only the blocks
        $C^{(j,l)}$ such that $\deg(q_j-q_l)<k$.

        A factorization algorithm could then be:
        \begin{einr}
          get the factor $f^{<k}$ common to both factorizations by truncation
          of $f^{\leq k}$ to terms of level $k$ and set
          $g^k:=(f^{<k})^{-1}f^{\leq k}$ and $f^k:=f^{\leq k}(f^{<k})^{-1}$.
        \end{einr}
      \end{s-rem}
    \item This decomposition in semidirect product can be extended to all
      levels (cf.\ \cite[Cor.I.5.2]{Loday1994}). Thus
      \[
        \Lambda(A^0)\cong\underset{k\in\cK}\bigltimes\Lambda^k(A^0) \,,
      \]
      where the semidirect product is taken in an ascending or descending
      order of levels $k$.
  \end{enumerate}
\end{cor}
\begin{rem}
  Loday-Richaud states in her paper \cite[Prop.I.5.3]{Loday1994} the following
  proposition.
  \begin{s-prop}
    \marginnote{\cite[Prop.I.5.3]{Loday1994}}
    For any levels $k$,$k'\in\cK$ with $k'<k$ one has:
    \begin{enumerate}
      \item the sheaf $\Lambda^{\geq k'}(A^0)\cap\Lambda^{\leq k'}(A^0)$ is
        normal in $\Lambda^{\leq k}(A^0)$;
      \item \marginnote{\cite[Proposition 10]{Martinet1991}}
        the exact sequence of sheaves
        \[
          1\longrightarrow\Lambda^{\geq k'}(A^0)\cap\Lambda^{\leq k'}(A^0)
          \overset{i}\longrightarrow\Lambda^{\leq k}(A^0)
          \overset{p}\longrightarrow\Lambda^{<k'}(A^0)
          \longrightarrow 1 \,,
        \]
        where
        \begin{itemize}
          \item $i$ is the canonical inclusion and
          \item $p$ is the truncation to terms of levels $<k'$,
        \end{itemize}
        splits.
    \end{enumerate}
    \TODO[is $\Lambda^{\geq k'}(A^0)\cap\Lambda^{\leq k}(A^0)=\Lambda^k(A^0)$
    and thus the first proposition a corollary of this?]
  \end{s-prop}
  We can use this proposition to follow (cf.\ \cite[Cor.I.5.4]{Loday1994}) that
  \begin{enumerate}
    \item
      the filtration
      \[
        \Lambda^{k_r}(A^0)
        =
        \Lambda^{\geq k_r}(A^0)
        \subset
        \Lambda^{\geq k_{r-1}}(A^0)
        \subset
        \cdots
        \subset
        \Lambda^{\geq k_{1}}(A^0)
        =
        \Lambda(A^0)
      \]
      is normal and
    \item we can use this to achieve the decomposition
      \[
        \Lambda(A^0)\cong\underset{k\in\cK}\bigltimes\Lambda^k(A^0)
      \]
      taken in an arbitrary order. In fact, one can also extend the algorithm
      from Remark~\ref{rem:algFactorization} to an arbitrary order of levels.
  \end{enumerate}
\end{rem}
\begin{prop}\label{prop:filtrationOfStokesGroup}
  \marginnote{\cite[Prop.I.5.5]{Loday1994}}
  The results can be restricted to the Stokes groups
  (cf.\ \cite[Prop.I.5.5]{Loday1994}). Thus, for $\alpha\in\A$, one has
  \[
    \Sto_\alpha(A^0)\cong\underset{k\in\cK_\alpha}\bigltimes\Sto_\alpha^k(A^0)
  \]
  the semidirect product being taken in an arbitrary order\comm{~(we will only
  be interested in the ascending order)}.
  \begin{s-defn}
    We will denote the map, wich gives the factors of this factorization by
    \[
      i_\alpha:
      \Sto_\alpha(A^0)
      \overset{\cong}\longrightarrow
      \prod_{k\in\cK_\alpha}\Sto_\alpha^k(A^0)\,,
    \]
    where the factorization is taken in ascending order.
  \end{s-defn}
  \begin{s-rem}\label{rem:filtrationOfStokesMats}
    Write $\rho_{\alpha}^k:\Sto^k_\alpha(A^0)\to\SSto^k_\alpha(A^0)$ for
    the \rewrite{restriction} of the map $\rho_{\alpha}$
    (cf.\ Proposition~\ref{prop:representation}) to the level $k$.
    \rewrite{Then, one can} denote the induced decomposition also by
    \[
      i_\alpha:
      \SSto_\alpha(A^0)
      \overset{\cong}\longrightarrow
      \prod_{k\in\cK_\alpha}\SSto_\alpha^k(A^0)
    \]
    and the corresponding diagram
    \[ \begin{tikzcd}
        \Sto_\alpha(A^0)
        \rar{i_\alpha}
        \dar{\rho_{\alpha}}
        & \prod_{k\in\cK_\alpha}\Sto_\alpha^k(A^0)\,,
        \dar{\prod_{k\in\cK}\rho_{\alpha}^k}
      \\\SSto_\alpha(A^0)
        \rar{i_\alpha}
        & \prod_{k\in\cK_\alpha}\SSto_\alpha^k(A^0)\,,
    \end{tikzcd} \]
    commutes.
    \PROBLEM[PROOF?]
  \end{s-rem}
\end{prop}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stokes structures: using Stokes groups}\label{sec:mainThm2}
\marginnote{\cite{Loday1994}, \cite[Thm.4.3.11]{Loday2014}
  \\and \cite{boalch,thboalch}
  \\and \cite{babbitt1989local}
  \\and \cite{BJL1979Birkhoff}
  \\and \cite[Chapter 4]{Martinet1991}}

The goal in this section is to prove that there is a bijective and natural map
\[
  h:\prod_{\alpha\in\A}\Sto_\alpha(A^0)\longrightarrow\St(A^0) \,.
\]
And since $\Sto_\alpha(A^0)$ has $\SSto_\alpha(A^0)$ as a faithful
representation, we also get the isomorphism
$\prod_{\alpha\in\A}\SSto_\alpha(A^0)\cong\St(A^0)$ as a corollary.
\TODO[This goes back to \cite{BJL1979Birkhoff}?]

Let us recall, that $\St(A^0)$ is defined to be $H^1(S^1;\Lambda(^0))$
(cf.\ Section~\ref{sec:mainThm1}).
The elements of $\prod_{\alpha\in\A}\Sto_\alpha(A^0)$ define in a canonical way
cocycles of the sheaf $\Lambda(A^0)$ (cf.\ Remark~\ref{rem:mapStoToCocy}),
called Stokes cocycles (cf.\ Definition~\ref{defn:stokesCocycle}).
In fact, will $h$ map such cocycles to the cohomology class, to which they
correspond.
Thus the statement, that $h$ is a bijection, is equivalent to the statement
that
\begin{einr}
  in each cohomology class of $\St(A^0)$ is an unique $1$-cocycle, which is a
  Stokes cocycle.
\end{einr}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Coverings}
To formulate the following theorem, we use the notion of cyclic coverings and
nerves of such coverings, which are defined as follows.

\begin{defn}
  \marginnote{\cite[Sec.II.1]{Loday1994} and \cite[Sec.II.3.1]{Loday1994}}
  Let $J$ be a finite set, identified to the finite set
  $\{1,\dots,p\}\subset\Z$.
  \begin{enumerate}
    \item A \emph{cyclic covering} of $S^1$ is a finite covering
      $\cU=\left(U_j=U(\theta_j,\epsilon_j)\right)_{j\in J}$ consisting of
      arcs, which satisfies that
      \begin{enumerate}
        \item $\tilde\theta_j < \tilde\theta_{j+1}$ for $j\in\{1,\dots,p-1\}$,
        \item $\tilde\theta_j-\frac{\epsilon_j}{2}\leq
          \tilde\theta_{j+1}-\frac{\epsilon_{j+1}}{2}$ for
          $j\in\{1,\dots,p-1\}$ and
          $\tilde\theta_p-\frac{\epsilon_p}{2}\leq
          \tilde\theta_{1}+2\pi-\frac{\epsilon_{1}}{2}$,
      \end{enumerate}
      where the $\tilde\theta_j\in [0,2\pi[$ are determinations of the
      $\theta_j\in S^1$.
      \begin{comment}
        \begin{enumerate}
          \item the $\theta_j$ are in ascending order with respect to the
            clockwise orientation of $S^1$;
          \item the $U_j\cap U_{j+1}$ have only one connected component when
            $\#J>2$;
          \item the $U_j$ are not encased by another arc, this means that the
            open sets $U_j\backslash U_l$ are connected for all $j,l\in J$.
        \end{enumerate}
      \end{comment}
    \item The \emph{nerve} of a cyclic covering $\cU=\{U_j;j\in J\}$ is the
      family $\dot\cU=\{\dot U_j;j\in J\}$ defined by:
      \begin{itemize}
        \item $\dot U_j=U_j\cap U_{j+1}$ when $\#J>2$,
        \item $\dot U_1$ and $\dot U_2$ the connected components of
          $U_1\cap U_2$ when $\#J=2$.
      \end{itemize}
      \begin{s-rem}
        The nerve of the cyclic covering
        $\cU=\left(U(\theta_j,\epsilon_j)\right)_{j\in J}$ is explicitly given
        by
        \[
          \dot\cU=\left(
            \left(\theta_{j+1}-\frac{\epsilon_{j+1}}{2},
            \theta_{j}+\frac{\epsilon_{j}}{2}\right)
          \right)_{j\in J} \,.
        \]
      \end{s-rem}
  \end{enumerate}
\end{defn}
The cyclic coverings correspond one-to-one to nerves of cyclic coverings. If
one starts with a nerve $\{\dot U_j \mid j\in J\}$, one obtains a cyclic
covering as $\cU=\{U_j \mid j\in J\}$ where the arc $U_j$ is the connected
clockwise hull from $\dot U_{j-1}$ to $\dot U_j$.

\begin{defn}
  A covering $\cV$ is said to \emph{refine} a covering $\cU$ if, to each open
  set $V\in\cV$ there is at least one $U\in\cU$ with $V\subset U$.
\end{defn}
\begin{prop}
  \marginnote{\cite[Prop.II.1.3]{Loday1994}}
  The covering $\cV$ refines $\cU$ if and only if the corresponding nerves
  $\dot\cU=\{\dot U_j\}$ and $\dot\cV=\{\dot V_l\}$ satisfy
  \begin{einr}
    each $\dot U_j$ contains at least one $\dot V_l$.
  \end{einr}
\end{prop}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The theorem}
\begin{comment}
  \begin{lem}
    Since the sections of the sheaf $\Lambda(A^0)$ are solutions of the system
    $[A^0,A^0]$ (cf.\ Definition~\ref{defn:StokesSheaf}),
    the theory of differential equations\PROBLEM[source?] tells us that
    \rewrite{sections extend uniquely}.
    Thus we can extend any germ $\phi_\theta\in\Lambda_\theta(A^0)$ uniquely to
    a section $\phi\in\Gamma(\Omega;\Lambda(A^0))$, where $\Omega$ is the
    maximal arc of definition around $\theta$.

    \PROBLEM[The flatness property implicitly satisfied?]
  \end{lem}
\end{comment}
\begin{rem}\label{rem:mapStoToCocy}
  \marginnote{\cite[868]{Loday1994}}
  Let $\{\theta_j\mid j\in J\}\subset S^1$ be a finite set and
  $\dot\phi=(\dot\phi_{\theta_j})_{j\in J}
  \in\prod_{j\in J}\Lambda_{\theta_j}(A^0)$ be a finite family of germs.
  In the following way, one can associate a cohomology class in $\St(A^0)$ to
  any $\dot\phi$:
  \begin{einr}
    let $\dot\phi_j$ be the function representing the germ
    $\dot\phi_{\theta_j}$ on its maximal arc of definition $\Omega_j$ around
    $\theta_j$.
    Then, for every cyclic covering $\cU=(U_j)_{j\in J}$ which satisfies
    $\dot U_j\subset \Omega_j$ for all $j\in J$, one can define the $1$-cocycle
    $(\dot\phi_{j|\dot U_j})_{j\in J}\in\Gamma(\dot\cU;\Lambda(A^0))$.
  \end{einr}
  To a different cyclic covering, satisfying the condition above, this
  construction yields a cohomologous $1$-cocycle, thus the induced map
  \[
    \prod_{j\in J}\Lambda_{\theta_j}(A^0)
    \longrightarrow
    H^1(S^1;\Lambda(A^0))=\St(A^0)
  \]
  is welldefined.
  \begin{comment}
    \begin{s-rem}
      Let $\dot\phi=(\dot\phi_{\theta})\in\Lambda_\theta(A^0)$ be a cocycle
      consisting only of an single element, which satisfies that the maximal
      arc of definition $\theta$ has opening less than $2\pi$.
      There can not exist a covering consisting of a single element $U$
      satisfying $U\subset\Omega$ and thus no map \dots
    \end{s-rem}
  \end{comment}
\end{rem}
\begin{defn}\label{defn:stokesCocycle}
  \marginnote{\cite[Def.II.1.8]{Loday1994}
    \\, \cite[4.3.10]{Loday2014}
    \\, \cite[Defn 6 on p 374]{Martinet1991}}
  Let $\nu=\#\A$ the number of all anti-Stokes directions and write
  $\A=\{\alpha_1,\dots,\alpha_\nu\}$.

  A \emph{Stokes cocycle} is a 1-cocycle $(\phi_j)_{j\in\{1,\dots,\nu\}}\in
  \prod_{j\in\{1,\dots,\nu\}}\Gamma(U_j;\Lambda(A^0))$ corresponding to some
  cyclic covering with nerve $\dot\cU=(\dot U_j)_{j\in\{1,\dots,\nu\}}$,
  which satisfies for every $j\in\{1,\dots,\nu\}$
  \begin{itemize}
    \item $\alpha_j\in\dot U_j$ and
    \item the germ $\phi_{\alpha_j}:=\phi_{j,\alpha_j}$ of $\phi_j$ at
      $\alpha_j$ is an element of $\Sto_{\alpha_j}(A^0)$.
  \end{itemize}
  \begin{s-rem}
    Since the sections in $\Gamma(\dot U_j;\Lambda(A^0))$ are uniquely
    determined as the extension of the germ at $\alpha_j$ have that the set of
    all Stokes cocycles can be identified with
    $\prod_{\alpha\in\A}\Sto_\alpha(A^0)$.
  \end{s-rem}
\end{defn}
We can use Remark~\ref{rem:mapStoToCocy} to obtain, in the case $J=\A$, a
mapping
\[ \begin{tikzcd}
    h:\prod_{\alpha\in\A}\Sto_\alpha(A^0)
    \rar[hook]&
    \prod_{\alpha\in\A}\Lambda_\alpha(A^0)
    \rar&
    \St(A^0),
\end{tikzcd} \]
which takes a Stokes cocycle to its corresponding cohomology class.
\begin{center}
  \begin{minipage}[t]{0.8\textwidth}
    \begin{tthm}\label{thm:mainThm2}
      The map
      \[ \begin{tikzcd}
          h:\prod_{\alpha\in\A}\Sto_\alpha(A^0) \rar& \St(A^0)
      \end{tikzcd} \]
      is a bijection and natural.
      \begin{s-rem}
        \marginnote{\cite[869]{Loday1994},\cite[Sec.III.3.3]{Loday1994}}
        Natural means that $h$ commutes to isomorphisms and constructions over
        systems or connections they represent.
      \end{s-rem}
    \end{tthm}
  \end{minipage}
\end{center}
From theorem~\ref{thm:mainThm2} and Proposition~\ref{prop:representation} we
get the following corollary.
\begin{cor}\label{cor:isomToChochN}
  \PROBLEM[mentioned twice]
  Using the isomorphisms from the Stokes groups to the group of all Stokes
  matrices (cf.\ Proposition~\ref{prop:representation}) we obtain
  \[
    \St(A^0) \cong \prod_{\alpha\in\A}\SSto_\alpha(A^0)
  \]
  which endows $\St(A^0)$ with the structure of an unipotent Lie group with the
  finite complex dimension
  $N:=\dim_\C\St(A^0)=\sum_{\alpha\in\A}\dim_\C\SSto_\alpha(A^0)$ where
  $\dim_\C\SSto_\alpha(A^0)=\sum_{q_j\underset{\alpha,\max}{\prec} q_l}
  n_j\cdot n_l$ (cf.~\cite[Sec.III.1]{Loday1994}).
  This can be rewritten in the following way:
  \begin{align*}
    N&=\sum_{\alpha\in\A}\sum_{q_j\underset{\alpha,\max}{\prec}q_l}n_j\cdot n_l
    \\&= \sum_{1\leq j,l\leq n}\deg(q_j-q_l)\cdot n_j\cdot n_l
    \\&=\sum_{\substack{1\leq j,l\leq n\\j<l}}2\cdot\deg(q_j-q_l)\cdot
      n_j\cdot n_l \,.
  \end{align*}
  \begin{s-rem}
    This number $N$ is known to be the \emph{irregularity} of $[\End A^0]$.
  \end{s-rem}
\end{cor}
\begin{comment}
  \marginnote{\cite[880f]{Loday1994}}
  We have also two structures of a linear affine variety on the set $\St(A^0)$.
  \begin{rem}
    Let $\sto_\alpha(A^0)$ be the Lie algebra corresponding to
    $\Sto_\alpha(A^0)$. The exponential map\footnote{This is not the map $\exp$
    from section~\ref{sec:mainThm1}.} induces an homomorphism
    $\exp:\sto_\alpha(A^0)\to\Sto_\alpha(A^0)$ and denote by $\ln=\exp^{-1}$
    the inverse map.
    \begin{enumerate}
      \item The \emph{tangent linear structure} is defined as \TODO
      \item Using the map
        \begin{align*}
          \sto_{\alpha}(A^0) &\overset{\id+\cdot}\longrightarrow
          \Sto_{\alpha}(A^0)
        \\\dot{f}_\alpha & \longmapsto \id+\dot{f}_\alpha \,.
        \end{align*}
    \end{enumerate}
  \end{rem}
\end{comment}

\begin{rem}
  To define the inverse map of $h$, one has to find in each cocycle in
  $\St(A^0)$ the Stokes cocycle. Loday-Richaud gives an algorithm in section
  II.3.4 of her paper~\cite{Loday1994}, which takes a cocycle over an arbitrary
  cyclic covering and outputs cohomologous Stokes cocycle and thus solves this
  problem.
\end{rem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Proof of Theorem~\ref{thm:mainThm2}}\label{sec:proofOfMatrixThm}
We will only look at the unramified case, for which we refer to
\cite[Sec.II.3]{Loday1994}.
The proof in the ramified case can be found in \cite[Sec.II.4]{Loday1994}.
We first have to introduce adequate coverings, which will be used in the proof.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adequate coverings}
\begin{defn}
  \marginnote{\cite[371]{Martinet1991} defines adapted coverings}
  Let $\star\in\{k,<k,\leq k,\dots\}$.
  A covering $\cU$ beyond which the inductive limit
  $\underset{\cU}{\underrightarrow{\lim}}H^1(\cU;\Lambda^\star(A^0))$ is
  stationary is said to be \emph{adequate} to describe
  $H^1(S^1;\Lambda^\star(A^0))$ or \emph{adequate} to $\Lambda^\star(A^0)$.
  \begin{comment}
    A covering $\cU$ is said to be \emph{adequate} to describe
    $H^1(S^1;\Lambda^\star(A^0))$ or \emph{adequate} to $\Lambda^\star(A^0)$ if
    for every element in
    $\underset{\cU}{\underrightarrow{\lim}}H^1(\cU;\Lambda^\star(A^0))$
    given by some covering $\cU'$ and an element of
    $\Gamma(\cU';\Lambda^\star(A^0))$
    there exists
    \begin{itemize}
      \item an element in $\Gamma(\cU;\Lambda^\star(A^0))$ and
      \item an common refinement of $\cU$ and $\cU'$
    \end{itemize}
    such that \PROBLEM[the elements are~?? on the refined covering.]
  \end{comment}

  In other words is a covering $\cU$ adequate, if and only if the canonical map
  \[
      \Gamma(\cU;\Lambda^\star(A^0))\longrightarrow H^1(S^1;\Lambda^\star(A^0))
  \]
  is surjective.\TODO[Proof? check??]
\end{defn}
The following proposition is in Loday-Richaud's paper~\cite{Loday1994} given as
Proposition II.1.7. It contains a simple characterization, which will be used
to see, that our defined coverings are adequate.
\begin{prop}\label{prop:adeqCovCondition}
  \marginnote{\cite[Prop.II.1.7]{Loday1994}}
  Let $k\in\cK_\alpha$.
  \begin{s-defn}
    Let $\alpha\in\A^k$.
    An arc $U(\alpha,\frac{\pi}{k})$ is called a \emph{Stokes arc of level $k$
    at $\alpha$}.
  \end{s-defn}
  A cyclic covering $\cU=(U_j)_{j\in J}$, which satisfies
  \begin{einr}
    for every $\alpha\in\A^k$ contains the Stokes arc $U(\alpha,\frac{\pi}{k})$
    at least one arc $\dot U_j$ from the nerve $\dot\cU$ of $\cU$
  \end{einr}
  is adequate to $\Lambda^k(A^0)$.

  The covering $\cU$ is adequate to $\Lambda^{\leq k}(A^0)$ (resp.\
  $\Lambda^{<k}(A^0)$) if it is adequate to $\Lambda^{k'}(A^0)$ for every
  $k'\leq k$ (resp.\ $k'<k$).
\end{prop}

Let $k\in\cK$.
We want to define the three cyclic coverings $\cU^{k}$, $\cU^{\leq k}$ and
$\cU^{<k}$ which will be adequate to $\Lambda^k(A^0)$, $\Lambda^{\leq k}(A^0)$
and $\Lambda^{<k}(A^0)$. Furthermore will the coverings be comparable at the
different levels.

\begin{enumerate}
  \item The first covering $\cU^{k}=\{\dot U_\alpha^k\mid\alpha\in\A^k\}$
    is the cyclic covering with nerve
    \[
      \dot\cU^k:=
      \left\{\dot U_\alpha^k=U(\alpha,\frac{\pi}{k})\mid\alpha\in\A^k\right\}
    \]
    consisting of all Stokes arcs of level $k$ for anti-Stokes directions
    bearing the level $k$.
\end{enumerate}

\begin{rem}\label{rem:superSectors}
  Boalch introduces in his publications~\cite[19]{boalch}
  and~\cite[Def.1.23]{thboalch} the notion of \emph{supersectors}, they are in
  the case of a single level $k$, defined as follows:
  \begin{einr}
    write the anti-Stokes directions as $\A=\{\alpha_1,\dots,\alpha_\nu\}$
    arranged according to the clockwise ordering, then is the $i$-th
    supersector defined as the arc
    \[
      \hat\Sect^k_i:=
        \left(\alpha_i-\frac{\pi}{2k},\alpha_{i+1}+\frac{\pi}{2k}\right) \,.
    \]
  \end{einr}
  This yields a cyclic covering $(\hat\Sect^k_i)_{i\in\{1,\dots,\nu\}}$ whose
  nerve is exactly $\dot\cU^k$ defined above.
  \begin{comment}
    \begin{center}
      \begin{tikzpicture}[scale=3]
        \node[] (zero) at (0,0) {};
        \draw[blue] (zero) circle (1cm);

        \fill[fill=green!20!white] (0,0) -- ({cos( 15 )},{sin( 15 )}) arc
          (15:85:1) -- cycle;

        \fill[fill=red!60!black] (0,0) -- ({cos( 15 )*0.5},{sin( 15 )*0.5}) arc
          (15:45:0.5) -- cycle;
        \fill[fill=red!60!black] (0,0) -- ({cos( 55 )*0.5},{sin( 55 )*0.5}) arc
          (55:85:0.5) -- cycle;

        \fill[fill=green!20!white] (0,0) -- ({cos( 15 )*0.4},{sin( 15 )*0.4}) arc
          (15:85:0.4) -- cycle;

        \node[green!40!black] at (1,1) {$\widehat\Sect_i$};

        \node[] (lft) at ({cos( 85 )},{sin( 85 )}) {};
        \node[] (rgt) at ({cos( 15 )},{sin( 15 )}) {};

        \draw[->,red!40!black] ({cos( 45 )},{sin( 45 )})
          to [out=35, in=25] (rgt);

        \draw[->,red!40!black] ({cos( 55 )},{sin( 55 )})
          to [out=65, in=75] (lft);

        \draw[thick,red!40!black,path fading=west] (0,0) -- +({cos( 85 )},{sin( 85 )});
        \draw[thick,red!40!black,path fading=west] (0,0) -- +({cos( 15 )},{sin( 15 )});
        \fill[red!40!black] ({cos( 85 )},{sin( 85 )}) circle (1pt);
        \fill[red!40!black] ({cos( 15 )},{sin( 15 )}) circle (1pt);

        \foreach \w/\str in {10/,
                             20/,
                             45/$\alpha_i$,
                             55/$\alpha_{i+1}$}
        {\draw (0,0) -- +({cos( \w )},{sin( \w )}) node[right] {\str};
         \fill[blue!20!white] ({cos( \w )},{sin( \w )}) circle (.7pt);
         \foreach \sep in {60,120,180,240,300}
         {\draw (0,0) -- +({cos( \w + \sep )},{sin( \w + \sep )});
          \fill[blue!20!white]
            ({cos( \w + \sep )},{sin( \w + \sep )}) circle (.7pt);
         }
        };


        \fill (zero) circle (1pt);
      \end{tikzpicture}
    \end{center}
  \end{comment}
\end{rem}
If we extend to several levels, the set
$\bigcup_k\left\{U(\alpha,\frac{\pi}{k})\mid\alpha\in\A^{k}\right\}$ is no
longer a nerve.
Hence we have to define the coverings $\cU^{\leq k}$ and $\cU^{<k}$ in a
different way.
Denote by
\[
  \left\{K_1<\cdots<K_s=k\right\}
  =\left\{\max\left(\cK_\alpha\cap[0,k]\right)\mid\alpha\in\A^{\leq k}\right\}
\]
the set of all \emph{$k$-maximum levels} for $\alpha\in\A^{\leq k}$.
\begin{enumerate}
  \setcounter{enumi}{1}
  \item The cyclic covering
    $\cU^{\leq k}=\left\{U_\alpha^{\leq k}\mid\alpha\in\A^{\leq k}\right\}$
    will be defined by induction.
    Let us assume that
    \begin{einr}
      the $\dot U_\alpha^{\leq k}$ are defined for all $\alpha\in\A^{\leq k}$
      with $k$-maximum level greater than $K_i$ such that their complete family
      is a nerve.
    \end{einr}
    Let
    \begin{itemize}
      \item $\alpha$ be a anti-Stokes direction with $k$-maximum level $K_i$
        and
      \item $\alpha^-$ (resp.\ $\alpha^+$) be the next anti-Stokes direction
        with $k$-maximum level greater then $K_i$ on the left (resp.\ on the
        right) and define $\dot U_{\alpha^-,\alpha^+}$ as the clockwise hull of
        the arcs $\dot U_{\alpha^-}^{\leq k}$ and $\dot U_{\alpha^+}^{\leq k}$
        already defined by induction.
        If there are no anti-Stokes directions with $k$-maximum level greater
        then $K_i$ we set $\dot U_{\alpha^-,\alpha^+}=S^1$.
    \end{itemize}
    We then set
    \[
      \dot U_\alpha^{\leq k}
        :=U\left(\alpha,\frac{\pi}{K_i}\right)\cap\dot U_{\alpha^-,\alpha^+}
    \]
    and the family of all $\dot U_\alpha^{\leq k}$ is a nerve.\PROBLEM[proof!]
    \begin{rem}
      If $\alpha$ has a $k$-maximum level equal to $k$ then is
      $\dot U_\alpha^{\leq k}$ equal to the Stokes arc
      $U\left(\alpha,\frac{\pi}{k}\right)=\dot U_\alpha^k$.
      \comm{\dots{}and then no $0$-cochain with level $k$ or $\geq k$ can
      exists on the covering $\cU^{\leq{k}}$.}
    \end{rem}
\end{enumerate}

\begin{enumerate}
  \setcounter{enumi}{2}
\item The last cyclic covering,
  $\cU^{<k}=\left\{U_{\alpha}^k\mid\alpha\in\A^{<k}\right\}$, is defined as
  $\cU^{<k}:=\cU^{\leq k'}$ where $k':=\max\{k''\in\cK\mid k''<k\}$.
\end{enumerate}

\begin{figure} %{{{
  \centering

  \def\kOne{7}
  \def\kTwo{10}
  \begin{tikzpicture}[scale=5] %{{{

    \newcommand{\myDrawArcA}[4]{%{{{
      % Parameter: radius , center , width , color
      \pgfmathsetmacro\hwdth{#3 / 2}
      \draw[#4]
        ({cos( #2 )},{sin( #2 )})
        --
        ({cos( #2 ) * #1 },{sin( #2 ) * #1 });
      \draw[ultra thick,#4]
        ({cos(#2 - \hwdth) * #1},{sin(#2 - \hwdth) * #1})
        arc
        ({#2 - \hwdth}:{#2 + \hwdth}:#1);
      \draw[dotted,#4]
        ({cos(#2 - \hwdth) * #1},{sin(#2 - \hwdth) * #1})
        --
        ({cos(#2 - \hwdth)},{sin(#2 - \hwdth)});
      \draw[dotted,#4]
        ({cos(#2 + \hwdth) * #1},{sin(#2 + \hwdth) * #1})
        --
        ({cos(#2 + \hwdth)},{sin(#2 + \hwdth)});
      \filldraw[white] ({cos(#2)},{sin(#2)}) circle (0.5pt);
      \filldraw[red] ({cos(#2)},{sin(#2)}) circle (0.2pt);
    }%}}}
    \newcommand{\myDrawArcB}[5]{%{{{
      % Parameter: radius , center , start , stop , color
      \draw[#5]
        ({cos( #2 )},{sin( #2 )})
        --
        ({cos( #2 ) * #1 },{sin( #2 ) * #1 });
      \draw[ultra thick,#5]
        ({cos( #3 ) * #1},{sin( #3 ) * #1})
        arc
        ({ #3 }:{ #4 }:#1);
      \draw[dotted,#5]
        ({cos( #3 ) * #1},{sin( #3 ) * #1})
        --
        ({cos( #3 )},{sin( #3 )});
      \draw[dotted,#5]
        ({cos( #4 ) * #1},{sin( #4 ) * #1})
        --
        ({cos( #4 )},{sin( #4 )});
      \filldraw[white] ({cos(#2)},{sin(#2)}) circle (0.5pt);
      \filldraw[red] ({cos(#2)},{sin(#2)}) circle (0.2pt);
    }%}}}

    \node (zero) at (0,0) {};
    \draw (zero) circle (1cm);

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %% Inner:
    \foreach \n/\mycol/\baseR in {\kOne/orange/0.8
                                 ,\kTwo/purple/0.9}
    {%{{{
      \pgfmathsetmacro\wdth{180/\n}
      \foreach \i in {1,2,...,\n}{%
        \pgfmathsetmacro\r{{\baseR + mod(\i+1,2)*0.05}}
        \pgfmathsetmacro\angl{\i* \wdth}
        \myDrawArcA{\r}{\angl}{\wdth}{\mycol}

        \pgfmathsetmacro\r{{\baseR + mod(\i + mod(\n+1,2),2)*0.05}}
        \pgfmathsetmacro\angl{\i* \wdth+180}
        \myDrawArcA{\r}{\angl}{\wdth}{\mycol}
      }
    }%}}}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %% Outer:
    \def\mycol{brown}
    \pgfmathsetmacro{\wdth}{180/\kTwo}
    \foreach \i in {1,2,...,\kTwo}{%
      \pgfmathsetmacro\r{{1.05 + mod(\i+1,2)*0.05}}
      \pgfmathsetmacro\angl{\i* \wdth}
      \myDrawArcA{\r}{\angl}{\wdth}{\mycol}

      \pgfmathsetmacro\r{{1.05 + mod(\i + mod(\kTwo+1,2),2)*0.05}}
      \pgfmathsetmacro\angl{\i* \wdth+180}
      \myDrawArcA{\r}{\angl}{\wdth}{\mycol}
    }
    \foreach \i in {1,2,...,\kOne}{%
      \foreach \j in {1,...,\kTwo}{%
        \pgfmathparse{\i/\kOne <= \j/\kTwo ? 0 : 1}
        \ifnum\pgfmathresult=0{%
          \pgfmathparse{\i/\kOne < \j/\kTwo ? 0 : 1}
          \ifnum\pgfmathresult=0{%
            \pgfmathsetmacro\r{{1.15 + mod(\i+1,2)*0.05}}
            \pgfmathsetmacro\center{\i/\kOne*180}
            \pgfmathsetmacro\start{(\i-0.5)*180/\kOne > (\j-1.5)*180/\kTwo
              ? (\i-0.5)*180/\kOne : (\j-1.5)*180/\kTwo}
            \pgfmathsetmacro\stop{(\i+0.5)*180/\kOne > (\j+0.5)*180/\kTwo
              ? (\j+0.5)*180/\kTwo : (\i+0.5)*180/\kOne}
            \myDrawArcB{\r}{\center}{\start}{\stop}{\mycol}

            \pgfmathsetmacro\r{{1.15 + mod(\i,2)*0.05}}
            \pgfmathsetmacro\center{\center+180}
            \pgfmathsetmacro\start{\start+180}
            \pgfmathsetmacro\stop{\stop+180}
            \myDrawArcB{\r}{\center}{\start}{\stop}{\mycol}
          }\fi
          \breakforeach
        }\fi
      }
    }

    \fill[white] (zero) circle (1.5pt);
    \fill (zero) circle (.7pt);
  \end{tikzpicture} %}}}
  \caption{The adequate coverings for an example with $\cK=\{\kOne,\kTwo\}$ and
    $\A=\left\{ \frac{j\cdot\pi}{k}\mid k\in\cK\text{, } j\in\N \right\}$.
    The anti-Stokes directions are marked by the \textcolor{red}{red} dots.
    The arcs of $\dot\cU^{\kOne}=\dot\cU^{\leq\kOne}$ are
    \textcolor{orange}{orange}, the arcs of $\dot\cU^{\kTwo}$ are
    \textcolor{purple}{purple} and the arcs of $\dot\cU^{\leq\kTwo}=\dot\cU$
    are \textcolor{brown}{brown}.
  }\label{fig:adequateCovering}
\end{figure}%}}}

\begin{rem}
  The coverings $\cU^{k}$, $\cU^{\leq k}$ and $\cU^{<k}$ depend only on
  $\cQ(A^0)$. Hence they depend only on the determining polynomials.
\end{rem}
It is obvious, that for every $k\in\cK$ the covering $\cU^{\leq k}$ refines
$\cU^{k}$ and $\cU^{<k}$.
Furthermore are the coverings defined, such that they satisfy the
condition in Proposition~\ref{prop:adeqCovCondition}.
Thus the first property in the following proposition is satisfied. The other
two can be found at \cite[Prop.II.3.1 (iv)]{Loday1994}.
\begin{prop}\label{prop:adequateProperties}
  \marginnote{\cite[Prop.II.3.1]{Loday1994}}
  \PROBLEM[Was bedeutet das?]
  Let $k\in\cK$, then
  \begin{enumerate}
    \item the coverings $\cU^{k}$, $\cU^{\leq k}$ and $\cU^{<k}$ are adequate
      to $\Lambda^k(A^0)$, $\Lambda^{\leq k}(A^0)$ and $\Lambda^{<k}(A^0)$;
    \item there exists no $0$-cochain in $\Lambda^k(A^0)$ on $\cU^k$;
    \item on $\cU^{\leq k}$ there is no $0$-cochain in $\Lambda^{\leq0}(A^0)$
      of level $k$, i.e.\ all $0$-cochains of $\Lambda^{\leq k}(A^0)$
      belong to $\Lambda^{<k}(A^0)$.
  \end{enumerate}
\end{prop}
To have a shorter notation, we denote the product
$\prod_{\alpha\in\A^\star}\Gamma(\dot U_\alpha^\star;\Lambda^\star(A^0))$ by
$\Gamma(\dot U^\star;\Lambda^\star(A^0))$ for every
$\star\in\{k,<k,\leq k,\dots\}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{The case of a unique level}
\marginnote{\cite[II.3.2]{Loday1994}}
First we will proof theorem~\ref{thm:mainThm2} in the case of a unique level.
This means that
\begin{itemize}
  \item either $\Lambda(A^0)$ has only one level $k$, thus
    \begin{itemize}
      \item $\Lambda(A^0)=\Lambda^k(A^0)$ and
      \item $\Sto_\theta(A^0)=\Sto_\theta^k(A^0)$ for every $\theta$,
    \end{itemize}
  \item or we restrict to a given level $k\in\cK$.
\end{itemize}
\begin{comment}
  \begin{lem}\label{lem:extendsSoFar}
    Every $k$-germ $\phi_\alpha\in\Lambda_\alpha^k(A^0)$ can be uniquely
    extended to the corresponding arc $U_\alpha^k$ in $\cU^k$.
    \begin{s-cor}
      For every $\alpha$ can every germ at $\phi_\alpha\in\Lambda_\alpha(A^0)$,
      with the levels $\cK(\phi_\alpha)$, be extended to the arc
      $\underset{U_\alpha}{%
        \underset{\text{\rotatebox[origin=c]{90}{$\subset$}}}{%
          U_\alpha^{\max\cK(\phi_\alpha)}}}\in\cU^{\max\cK(\phi_\alpha)}$.
    \end{s-cor}
  \end{lem}
  Since the sheaf $\hat\SSto(A^0)$ is locally constant with discontinuities at
  the Stokes directions.
\end{comment}
\begin{comment}
  \begin{lem}\label{lem:extendsSoFar}
    Every $k$-germ $\phi_\alpha\in\Lambda_\alpha^k(A^0)$ can be uniquely
    extended to the corresponding arc $U_\alpha^k$ in $\cU^k$.
    \begin{s-cor}
      For every $\alpha$ can every germ at $\phi_\alpha\in\Lambda_\alpha(A^0)$,
      with the levels $\cK(\phi_\alpha)$, be extended to the arc
      $\underset{U_\alpha}{%
        \underset{\text{\rotatebox[origin=c]{90}{$\subset$}}}{%
          U_\alpha^{\max\cK(\phi_\alpha)}}}\in\cU^{\max\cK(\phi_\alpha)}$.
    \end{s-cor}
  \end{lem}
  \begin{lem}
    The extension is linear, i.e.\ is the extension of a sum the sum of the
    extensions. Especially
    \begin{einr}
      let $\phi_\alpha\in\Sto_\alpha(A^0)$ be a germ \dots
    \end{einr}
  \end{lem}
  \begin{rem}
    The uniqueness from lemma~\ref{lem:extendsSoFar} is clear, since the
    sections of $\Lambda^k(A^0)$ are solution of the system $[A^0,A^0]$ and it
    is very well known from the theory of differential equations\TODO[source?]
    that an element $f_\alpha\in\Gamma(\dot\cU_\alpha^k;\Lambda^k(A^0))$ is
    uniquely determined as the extension of its germ at some point $\alpha$.
  \end{rem}
  It remains to see that the germs $\phi_\alpha$ can be extended to the arc
  $U_\alpha^k$, which is delimited by the corresponding Stokes directions.
  There may be a direct way, without using summation theory, but this is
  only implicitly mentioned in Loday-Richaud's paper~\cite{Loday1994}.
  We will instead use the two theorems~\cite[Thm.4.3.13]{Loday2014}
  \marginnote{(or~\cite[Prop.III.2.1]{Loday1994},
              \cite[Thm.1]{BJL1979Birkhoff})}
  and~\cite[Thm.3.1 2]{boalch}. The first explains, how the Stokes cocycles
  are connected to the theory of summation and the second gives an statement
  how far the obtained sums can be analytically extended.

  Denote by $\alpha^+$ (resp.\ $\alpha^-$) the next anti-Stokes direction on
  the right (resp.\ left) of $\alpha$.
  \begin{thm}
    Let $\hat F\in\hat G(A^0)$ be an formal transformation.
    On each arc $(\alpha,\alpha^+)$ the summation theory gives a canonical way
    to find an invertible $n\times n$ matrix of meromorphic functions
    $\Sigma_i(\hat F)$ asymptotic to $\hat F$, which is called \emph{the sum of
    $\hat F$}.
  \end{thm}
  \begin{defn}\label{defn:sumsLeftRight}
    \marginnote{\cite[Defn.III.2.2]{Loday1994}}
    Denote by $\alpha^+$ the next anti-Stokes direction on the right of $\alpha$
    we can define
    \begin{itemize}
      \item $S_\alpha^-(\hat F):=F_\alpha$ as the \emph{sum of $\hat F$ on the
        left of $\alpha$} and
      \item $S_\alpha^+(\hat F):=F_{\alpha^+}$ as the \emph{sum of $\hat F$ on
        the right of $\alpha$}.
    \end{itemize}
  \end{defn}
  \begin{lem}
    \marginnote{\cite[Thm.4.3.13]{Loday2014}}
    The Stokes cocycle $(\phi_\alpha)_{\alpha\in\A}$ satisfy
    \[
      \phi_\alpha=F_\alpha^+(t)^{-1}F_\alpha^-(t) \,.
    \]
  \end{lem}
  \begin{lem}
    \marginnote{\cite[Thm.3.1]{boalch}}
    Let $\pm\in\{+,-\}$ and let $\Omega_\alpha^\pm\ni\alpha$ be the arc of
    definition of $F_\alpha^\pm(t)$.
    The sum $F_\alpha^\pm(t)$ can be analytically continued to the arc
    $U_\alpha^k\cup\Omega_\alpha^\pm$.
  \end{lem}


  Let us now look closer at the canonical extension
  \[ \begin{tikzcd}
    i^k:\underset{\alpha\in\A}\prod\Sto_\alpha^k(A^0) \rar&
    \Gamma(\dot\cU^k;\Lambda^k(A^0)) \,,
  \end{tikzcd} \]
  which extends every germ $\phi_\alpha\in(\phi_\alpha)_{\alpha\in\A}$ to
  the corresponding arc $U_\alpha\in\dot\cU^k$.
\end{comment}
\begin{lem}
  Let $k\in\cK$.
  The morphism $h$ from Theorem~\ref{thm:mainThm2} is in the case of an unique
  level build as
  \[ \begin{tikzcd}[row sep=0cm]
    \underset{\alpha\in\A}\prod\Sto_\alpha^k(A^0)
    \rar{i^k}
    & \Gamma(\dot\cU^k;\Lambda^k(A^0))
    \rar{s^k}
    & H^1(S^1;\Lambda^k(A^0))
    \\
    \text{\rotatebox[origin=c]{-90}{$=$}}
    &&
    \text{\rotatebox[origin=c]{-90}{$=$}}
    \\
    \underset{\alpha\in\A}\prod\Sto_\alpha(A^0)
    \arrow{rr}{h}
    &
    & H^1(S^1;\Lambda(A^0))
  \end{tikzcd} \]
  from
  \begin{itemize}
    \item the canonical injective map
      \[ \begin{tikzcd}
        i^k:\underset{\alpha\in\A}\prod\Sto_\alpha^k(A^0) \rar&
        \Gamma(\dot\cU^k;\Lambda^k(A^0)) \,,
      \end{tikzcd} \]
      i.e.\ the map which is the canonical extension of germs to their natural
      arc of definition, and
    \item the quotient map
      \[ \begin{tikzcd}
        s^k:\Gamma(\dot\cU^k;\Lambda^k(A^0)) \rar& H^1(S^1;\Lambda^k(A^0))
      \end{tikzcd} \]
  \end{itemize}
  which are both isomorphisms.
\end{lem}
\begin{proof}
  \begin{enumerate}
    \item The map
      \[ \begin{tikzcd}
        i^k: \underset{\alpha\in\A}\prod\Sto_\alpha^k(A^0)
        \rar &
        \underset{\Gamma(\dot\cU^k;\Lambda^k(A^0))}{%
          \underset{\text{\rotatebox[origin=c]{-90}{$=$}}}{%
            \underbrace{%
              \prod_{\alpha\in\A^k}\Gamma(\dot\cU_\alpha^k;\Lambda^k(A^0))
            }
        }}
      \end{tikzcd} \]
      is welldefined, since the sections of $\Lambda^k(A^0)$ are solution of
      the system $[A^0,A^0]$ and it is very well known from the theory of
      differential equations\TODO[source?] that an element
      $f_\alpha\in\Gamma(\dot\cU_\alpha^k;\Lambda^k(A^0))$ is uniquely
      determined as the extension of its germ at some point $\alpha$.

      It is also a group isomorphism (cf.~\cite{Loday1994}).

      \PROBLEM[$\Sto_\alpha^k(A^0)\subsetneq\Lambda_\alpha^k(A^0)$ SEE bjl p.72]
      \begin{comment}
        It is a group isomorphism, since
        \\Problems:
        \begin{itemize}
          \item Show that a element of $\Lambda_\alpha^k(A^0)$ is extensionable
            to the arc $U_\alpha\in\dot\cU_\alpha^k$ if and only if it has
            maximal decay in direction $\alpha$.
          \item \PROBLEM[$\Sto_\alpha^k(A^0)\subsetneq\Lambda_\alpha^k(A^0)$]
            and thus
            \[
              i^k:
              \underset{\alpha\in\A}\prod\Sto_\alpha^k(A^0)
              \subsetneq
              \underset{\alpha\in\A}\prod\Lambda_\alpha^k(A^0)
              \to
              \prod_{\alpha\in\A^k}\Gamma(\dot\cU_\alpha^k;\Lambda^k(A^0))
            \]
        \end{itemize}
        IDEAS:
        \begin{itemize}
          \item Are sections fully determined by there germs at some points?
            \begin{itemize}
              \item since sections are defined by differential equations??

                ODE-Theory, says that a germ defines a solution in a
                \textbf{neighbourhood}
              \item \PROBLEM[why is the neighbourhood large enough?] I.e.\
                \[
                  \substack{the\\neighbourhood}\supset\cU_\alpha^k \,?
                \]
            \end{itemize}
          \item $U_\alpha^k$ is the largest arc, to contain no corresponding
            Stokes ray
            \begin{itemize}
              \item Then might \cite[Lemma 1]{BJL1979Birkhoff} on p.\ 73 help
            \end{itemize}
          \item Every arc $U\in\dot\cU_\alpha^k$ has the width $\frac{\pi}{k}$
            and is delimited by Stokes directions.
          \item maybe follows from \cite[Prop.1.24]{thboalch}
          \item \textbf{See \cite{babbitt1989local}}
          \item See \cite[375]{Martinet1991} and
            \cite[Def.5 on 372]{Martinet1991}
        \end{itemize}
      \end{comment}
    \item The second map
      \[ \begin{tikzcd}
        s^k:
        \overset{\Gamma(\dot\cU^k;\Lambda^k(A^0))}{%
          \overset{\text{\rotatebox[origin=c]{-90}{$=$}}}{%
            \overbrace{%
              \prod_{\alpha\in\A^k}\Gamma(\dot\cU_\alpha^k;\Lambda^k(A^0))
            }
        }}
        \rar &
        H^1(S^1;\Lambda^k(A^0))
      \end{tikzcd} \]
      is a bijection, \rewrite{since} from
      proposition~\ref{prop:adequateProperties} we know that it is
      \begin{itemize}
        \item \textbf{surjective}, \rewrite{since} $\cU^k$ is adequate to
          $\Lambda^k(A^0)$ and
        \item \textbf{injective}, \rewrite{since} on $\cU^k$ there is no
          $0$-cochain in $\Lambda^k(A^0)$.
      \end{itemize}
  \end{enumerate}
  \PROBLEM[Show that this is the correct $h$]
  \PROBLEM[Naturality?]
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{The case of several levels}
\rewrite{In the proof of the case of several levels, we will still use}
Loday-Richaud's paper~\cite{Loday1994} as reference.
\begin{defn}\label{defn:firstSetOfInlusions}
  Here we want to define a \emph{product map of cocycles}
  $\mathfrak{S}^{\leq k}$.
  This map will be composed from the following injective maps:
  \begin{enumerate}
    \item The first map is defined as
      \begin{align*}
        \sigma^k:\Gamma(\dot\cU^k;\Lambda^k(A^0))
        &\longrightarrow \Gamma(\dot\cU^{\leq k};\Lambda^{\leq k}(A^0))
      \\\dot f=(\dot f_\alpha)_{\alpha\in\A^k}
        &\longmapsto (\dot G_\alpha)_{\alpha\in\A^{\leq k}}
      \end{align*}
      where
      \begin{itemize}
        \item $\dot G_\alpha=\begin{cases}
            \dot f_\alpha \text{~restricted to } \dot U_\alpha^{\leq k}
            \text{~and seen as being in } \Lambda^{\leq k}(A^0)
            & \text{~when } \alpha\in\A^k
          \\\id \text{~(the identity) }
            & \text{~when } \alpha\notin\A^k
          \end{cases}$
      \end{itemize}
    \item and the second map
      \begin{align*}
        \sigma^{<k}:\Gamma(\dot\cU^{<k};\Lambda^{<k}(A^0))
        &\longrightarrow \Gamma(\dot\cU^{\leq k};\Lambda^{\leq k}(A^0))
      \\\dot f=(\dot f_\alpha)_{\alpha\in\A^{<k}}
        &\longmapsto (\dot F_\alpha)_{\alpha\in\A^{\leq k}}
      \end{align*}
      is defined, in a similar way, as
      \begin{itemize}
        \item $\dot F_\alpha=\begin{cases}
            \dot f_\alpha \text{~restricted to } \dot U_\alpha^{\leq k}
            \text{~and seen as being in } \Lambda^{\leq k}(A^0)
            & \text{~when } \alpha\in\A^{<k}
          \\\id \text{~(the identity) }
            & \text{~when } \alpha\notin\A^{<k}
          \end{cases}$
      \end{itemize}
  \end{enumerate}
  Thus we can define
  \begin{align*}
    \mathfrak{S}^{\leq k}:
    \Gamma(\dot\cU^{<k};\Lambda^{<k}(A^0))
    \times
    \Gamma(\dot\cU^{k};\Lambda^{k}(A^0))
    &\longrightarrow
    \Gamma(\dot\cU^{\leq k};\Lambda^{\leq k}(A^0))
  \\(\dot f, \dot g)
    &\longmapsto
    (\dot F_\alpha\dot G_\alpha)_{\alpha\in\A^{\leq k}}
  \end{align*}
  where $(\dot F_\alpha)_{\alpha\in\A^{\leq k}}=\sigma^{<k}(\dot f)$ and
  $(\dot G_\alpha)_{\alpha\in\A^{\leq k}}=\sigma^k(\dot g)$ are defined as
  above.
  \begin{s-rem}
    This map $\mathfrak{S}^{\leq k}$ is injective, since injectivity for germs
    implies injectivity for sections.
  \end{s-rem}
\end{defn}

\begin{lem}
  \marginnote{\cite[Lem.II.3.3]{Loday1994}}
  Let $k\in\cK$.
  \begin{enumerate}
    \item If the cocycles $\mathfrak{S}^{\leq k}(\dot f,\dot g)$ and
      $\mathfrak{S}^{\leq k}(\dot f',\dot g')$ are cohomologous in
      $\Gamma(\dot\cU^{\leq k};\Lambda^{\leq k}(A^0))$
      then $\dot f$ and $\dot f'$ are cohomologous in
      $\Gamma(\dot\cU^{<k};\Lambda^{<k}(A^0))$.
    \item Any cocycle in $\Gamma(\dot\cU^{\leq k},\Lambda^{\leq k}(A^0))$ is
      cohomologous to a cocycle in the range of $\mathfrak{S}^{\leq k}$.
  \end{enumerate}
\end{lem}
\begin{proof}
  \begin{enumerate}
    \item Denote by $\alpha^+$ the nearest anti-Stokes direction in
      $\A^{\leq k}$ on the right\footnote{In clockwise direction.} of $\alpha$.
      The cocycles $\mathfrak{S}^{\leq k}(\dot f,\dot g)$ and
      $\mathfrak{S}^{\leq k}(\dot f',\dot g')$ are cohomologous if and only
      if there is a $0$-cochain $c=(c_\alpha)_{\alpha\in\A^{\leq k}}
      \in\Gamma(\cU^{\leq k},\Lambda^{\leq k}(A^0)$ such that
      \begin{equation}\label{eq:UniqueString:urdtindfgupndtcn}
        \dot F_\alpha\dot G_\alpha =
        c_\alpha^{-1}\dot F_\alpha'\dot G_\alpha'c_{\alpha^+}
      \end{equation}
      for every $\alpha\in\A$. From Proposition~\ref{prop:adequateProperties}
      follows, that $c$ is with values in $\Lambda^{<k}(A^0)$.
      The fact that $\Lambda^k(A^0)$ is normal in $\Lambda^{\leq k}(A^0)$ in
      Proposition~\ref{prop:PropertiesOfStokesSheafSplitting}, can be used to
      see that $ c_{\alpha^+}^{-1}G_\alpha'c_{\alpha^+}
      \in\Gamma(\cU^{\leq k};\Lambda^{k}(A^0))$.
      Thus, we rewrite the relation (\ref{eq:UniqueString:urdtindfgupndtcn}) to
      \[
        \dot F_\alpha\dot G_\alpha =
        (c_\alpha^{-1}\dot F_\alpha'c_{\alpha^+})
        (c_{\alpha^+}^{-1}G_\alpha'c_{\alpha^+})
        \,,\qquad\text{~for~} \alpha\in\A^{\leq k} \,.
      \]
      Since Corollary~\ref{cor:factorStokesGerms} tells us, that the
      factorization into the factors of the semidirect product are unique, we
      get for all $\alpha\in\A^k$
      \[
        \dot F_\alpha=c_\alpha^{-1}\dot F_\alpha'c_{\alpha^+}
        \qquad \text{~and~} \qquad
        \dot G_\alpha=c_{\alpha^+}^{-1}\dot G_\alpha'c_{\alpha^+}.
      \]
      The former relation implies that $(\dot F_\alpha)$ and $(\dot F_\alpha')$
      are cohomologous with values in $\Lambda^{<k}(A^0)$ on $\cU^{\leq k}$.
      Since $\cU^{<k}$ is already adequate to $\Lambda^{<k}(A^0)$, \rewrite{are
      $(\dot F_\alpha)$ and $(\dot F_\alpha')$} already on $\cU^{<k}$,
      i.e.\ in $\Gamma(\dot\cU^{<k};\Lambda^{<k}(A^0))$, cohomologous.
    \item The proof of part 2.\ (together with a proof of part 1.) can be
      found in Loday-Richaud's paper \cite[Proof of Lem.II.3.3]{Loday1994}.
  \end{enumerate}
\end{proof}
Let $k\in\cK$ and $k'=\max\{k'\in\cK\mid k'<k\}$. We then know by definition
that $\cU^{<k}=\cU^{\leq k'}$ as well as
$\Lambda^{< k}(A^0)=\Lambda^{\leq k'}(A^0)$ and thus
$\Gamma(\dot\cU^{< k};\Lambda^{< k}(A^0))=
\Gamma(\dot\cU^{\leq k'};\Lambda^{\leq k'}(A^0))$ and obtain the following
proposition.
\begin{prop}\label{prop:theMapTau}
  By applying $\mathfrak{S}^{\leq\star}$ multiple times one obtains
  the \emph{product map of single leveled cocycles} in the following way
  \[ \begin{tikzcd}[column sep=1.4cm,row sep=.9cm]
      \underset{\tikzmark{e1}}{\underbrace{%
        \Gamma(\dot\cU^{<k_r};\Lambda^{<k_r}(A^0))}}
      \times
      \Gamma(\dot\cU^{k_r};\Lambda^{k_r}(A^0))
      \rar{\mathfrak{S}^{\leq k_r}}&
      \overset{\Gamma(\dot\cU;\Lambda(A^0))}{%
        \overset{\text{\rotatebox[origin=c]{-90}{$=$}}}{%
          \Gamma(\dot\cU^{\leq k_r};\Lambda^{\leq k_r}(A^0))
      }}
      \\\underset{\tikzmark{e2}}{\underbrace{%i
        \Gamma(\dot\cU^{<k_{r-1}};\Lambda^{<k_{r-1}}(A^0))}}
      \times
      \Gamma(\dot\cU^{k_{r-1}};\Lambda^{k_{r-1}}(A^0))
      \rar{\mathfrak{S}^{\leq k_{r-1}}}&
      \overset{\tikzmark{n1}}{%
        \Gamma(\dot\cU^{\leq k_{r-1}};\Lambda^{\leq k_{r-1}}(A^0))}
      \\\hspace{6cm}\cdots \rar{\mathfrak{S}^{\leq k_{r-2}}}&
      \overset{\tikzmark{n2}}{%
        \Gamma(\dot\cU^{\leq k_{r-2}};\Lambda^{\leq k_{r-2}}(A^0))}
      \\\underset{\tikzmark{eEND}}{\underbrace{%
        \Gamma(\dot\cU^{<k_3};\Lambda^{<k_3}(A^0))}}
      \times
      \Gamma(\dot\cU^{k_3};\Lambda^{k_3}(A^0))
      \rar{\mathfrak{S}^{\leq k_3}}&
      \cdots\hspace{3cm}
      \\
      \Gamma(\dot\cU^{k_1};\Lambda^{k_1}(A^0))
      \times
      \Gamma(\dot\cU^{k_2};\Lambda^{k_2}(A^0))
      \rar{\mathfrak{S}^{\leq k_2}}&
      \overset{\tikzmark{nEND}}{%
        \Gamma(\dot\cU^{\leq k_2};\Lambda^{\leq k_2}(A^0))}
  \end{tikzcd} \]
  \begin{tikzpicture}[remember picture,overlay]
    \draw[<-] (n1) to[out=90,in=270] node[midway,fill=white]{$=$}
      ([yshift=.3em]e1);
    \draw[<-] (n2) to[out=90,in=270] node[midway,fill=white]{$=$}
      ([yshift=.3em]e2);
    \draw[<-] (nEND) to[out=90,in=270] node[midway,fill=white]{$=$}
      ([yshift=.3em]eEND);
  \end{tikzpicture}
  which can be written in the following compact form
  \begin{align*}
    \tau:\prod_{k\in\cK}\Gamma(\dot \cU^k;\Lambda^k(A^0))
    &\longrightarrow
    \Gamma(\dot\cU;\Lambda(A^0))
  \\(\dot f^k)_{k\in\cK}
    &\longmapsto
    \prod_{k\in\cK}\tau^k(\dot f^k)
  \end{align*}
  where the products are following an ascending order of levels and the maps
  $\tau_k$ are defined as
  \[ \begin{tikzcd}[row sep=0cm]
    \tau^k:\Gamma(\dot\cU^k;\Lambda^k(A^0))
    \arrow{r}{\sigma^k}&
    \Gamma(\dot\cU^{\leq k};\Lambda^{\leq k}(A^0))
    \rar &
    \Gamma(\dot\cU;\Lambda(A^0))
  \\~~~(\dot f_\alpha)_{\alpha\in\A^k}
    \arrow[|->]{rr}
    &&
    (\dot F_\alpha)_{\alpha\in\A}
  \end{tikzcd} \]
  with
  \[
    \dot F_\alpha=\begin{cases}
      \dot f_\alpha \text{~restricted to } \dot U_\alpha
      \text{~and seen as being in } \Lambda(A^0)
      & \text{~when } \alpha\in\A^k
    \\\id \text{~(the identity on $\dot U_\alpha$) }
      & \text{~when } \alpha\notin\A^k
    \end{cases}
  \]
  The defined map $\tau$ is clearly injective and it can be extended to an
  arbitrary order of levels (cf.\ Remark~\cite[Rem.II.3.5]{Loday1994}).
\end{prop}
\begin{comment}
  \begin{defn}\label{defn:theMapTau}
    Define the injective map
    \begin{align*}
      \tau^k:\Gamma(\dot\cU^k;\Lambda^k(A^0))
      &\longrightarrow \Gamma(\dot\cU;\Lambda(A^0))
    \\\dot f=(\dot f_\alpha)_{\alpha\in\A^k}
      &\longmapsto
      (\dot F_\alpha)_{\alpha\in\A}
    \end{align*}
    where
    \[
      \dot F_\alpha=\begin{cases}
        \dot f_\alpha \text{~restricted to } \dot U_\alpha
        \text{~and seen as being in } \Lambda(A^0)
        & \text{~when } \alpha\in\A^k
      \\\id \text{~(the identity on $\dot U_\alpha$) }
        & \text{~when } \alpha\notin\A^k
      \end{cases}
    \]
    \marginnote{\cite[Prop.II.3.4]{Loday1994}}
    The \emph{product map of single-leveled cocycles} is then defined as
    \begin{align*}
      \tau:\prod_{k\in\cK}\Gamma(\dot \cU^k;\Lambda^k(A^0))
      &\longrightarrow
      \Gamma(\dot\cU;\Lambda(A^0))
    \\(\dot f^k)_{k\in\cK}
      &\longmapsto
      \prod_{k\in\cK}\tau^k(\dot f^k)
    \end{align*}
    following an ascending order of levels.
    \begin{s-rem}
      The map $\tau$
      \begin{enumerate}
        \item is injective since it is composed from $\sigma^k$ and the clearly
          injetive mapping
          \begin{align*}
            \Gamma(\dot\cU^{\leq k};\Lambda^{\leq k}(A^0))
            &\longrightarrow
            \Gamma(\dot\cU;\Lambda(A^0))
          \\(\dot F_\alpha)_{\alpha\in\A^{\leq k}}
            &\longmapsto
            (\dot F'_\alpha)_{\alpha\in\A}
          \end{align*}
          where
          \[
            \dot F'_\alpha=\begin{cases}
              \dot F_\alpha \text{~restricted to } \dot U_\alpha
              \text{~and seen as being in } \Lambda(A^0)
              & \text{~when } \alpha\in\A^{\leq k}
              \\\id \text{~(the identity on $\dot U_\alpha$) }
              & \text{~when } \alpha\notin\A^{\leq k}
            \end{cases}
          \]
          and
        \item it can be extended to an arbitrary order of levels
          (cf.\ Remark~\cite[Rem.II.3.5]{Loday1994}).
      \end{enumerate}
    \end{s-rem}
  \end{defn}
\end{comment}
\begin{cor}
  The product map of single-leveled cocycles $\tau$ induces on the cohomology
  a bijective and natural map
  \[ \begin{tikzcd}
    \cT:
    \underset{\underset{k\in\cK}\prod H^1(S^1;\Lambda^k(A^0))}{%
      \underset{\text{\rotatebox[origin=c]{-90}{$\cong$}}}{%
        \prod_{k\in\cK}\Gamma(\dot\cU^k;\Lambda^k(A^0))}}
    \rar&
    \underset{H^1(S^1;\Lambda(A^0))}{%
      \underset{\text{\rotatebox[origin=c]{-90}{$\cong$}}}{%
        H^1(\cU;\Lambda(A^0))}}\,.
  \end{tikzcd} \]
\end{cor}
\paragraph{Composing functions to obtain $h$}
We have the ingredients to define the function $h$ from
Theorem~\ref{thm:mainThm2} by composition of already bijective maps.
\begin{proof}[Proof of theorem~\ref{thm:mainThm2}]
  Let $i_\alpha:\Sto_\alpha(A^0)\to\prod_{k\in\cK}\Sto_\alpha^k(A^0)$ be the
  map which corresponds to the filtration from
  proposition~\ref{prop:filtrationOfStokesGroup} and
  denote the composition
  \[ \begin{tikzcd}[column sep=1.8cm,row sep=0]
      \displaystyle \prod_{\alpha\in\A}\Sto_\alpha(A^0)
      \rar{\prod_{\alpha\in\A}i_\alpha}
      \arrow[ddrr, out=270,in=200,"\mathfrak{T}"]
      &
      \displaystyle \prod_{\alpha\in\A}\prod_{k\in\cK}\Sto_\alpha^k(A^0)
    \\&\text{\rotatebox[origin=c]{-90}{$\equiv$}}
    \\&\displaystyle \prod_{k\in\cK}\prod_{\alpha\in\A}\Sto_\alpha^k(A^0)
      \rar{\prod_{k\in\cK}i^k}&
      \displaystyle \prod_{k\in\cK}\Gamma(\dot\cU^k;\Lambda^k(A^0))
  \end{tikzcd} \]
  by $\mathfrak{T}$. The bijection $h$ is then obtained as
  \[
    \cT\circ\mathfrak{T}: \prod_{\alpha\in\A}\Sto_\alpha(A^0)
    \longrightarrow H^1(\cU;\Lambda(A^0)) \,.
  \]
  \PROBLEM[naturality (is obvious?)]
  \PROBLEM[Show that this is the correct $h$]
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Further improvements}\label{sec:furtherImprovements}
The set $\prod_{\alpha\in\A}\Sto_\alpha(A^0)$ and thus
$\prod_{\alpha\in\A}\SSto_\alpha(A^0)$ has some bad properties, when small
deformations are applied to $[A^0]$, since under arbitrary small changes, one
Stokes ray can split into two.
\begin{comment}
  \begin{rem}\label{rem:boalchRemarkFactorMatrix}
    Boalch~\cite{boalch,thboalch}\PROBLEM[solution goes back to
    \cite{BJL1979Birkhoff} or so?] solves this in the single-leveled case by
    \rewrite{renaming our Stokes matrices as Stokes factors} and introducing
    new Stokes matrices which are build by the product of consecutive Stokes
    factors.
  \end{rem}
\end{comment}
In the prove of theorem~\ref{thm:mainThm2} we have seen, \rewrite{that not only
$\cH(A^0)\cong\prod_{\alpha\in\A}\Sto_\alpha(A^0)$ but} also that
\begin{align*}
  \cH(A^0)&\cong\prod_{k\in\cK}\prod_{\alpha\in\A}\Sto_\alpha^k(A^0)
  \\&\cong\prod_{k\in\cK}\prod_{\alpha\in\A^k}\Sto_\alpha^k(A^0)
  &\text{(since $\SSto_{\alpha}^{k}(A^0)=\{\id\}$ when $k\notin\cK_\alpha$.)}
  \\&\cong\prod_{k\in\cK}\prod_{\alpha\in\A^k}\SSto_\alpha^k(A^0) \,.
\end{align*}
This representation can be used to achieve further improvements, since one is
able to multiply some succeeding Stokes matrices (resp. Stokes germs) of the
same level without loss of information.
This is based on the Corollary~\ref{cor:composeLevelwise} stated bellow

Let us fix a level $k\in\cK$. We want to rewrite the product
$\prod_{\alpha\in\A^k}\SSto_\alpha^k(A^0)$ by collecting the information of
multiple Stokes matrices into one product of these matrices.

\TODO[move?]
Boalch, which looks in his publications \cite{boalch,thboalch} only at the
single-leveled case, uses this extensively to obtain better Stokes matrices,
which are stable under small deformations
(cf.\ Remark~\ref{rem:boalchRemarkFactorMatrix}).

\begin{defn}
  A subset of $\A^k$ consisting of $\frac{\#\A^k}{2k}$ consecutive anti-Stokes
  directions of level $k$ will be called a \emph{half-period (of level $k$)}.
  \begin{s-rem}
    The set $\A^k$ can clearly be split into $2k$ distinct half-periods.
  \end{s-rem}
\end{defn}
From the definition of anti-Stokes directions of level $k$ it is clear that
every arc of width $\frac{\pi}{k}$, which has no anti-Stokes direction of level
$k$ on its border, contains $\frac{\#\A^k}{2k}$ anti-Stokes directions
since
\begin{einr}
  for every sector $I=U(\theta,\frac{\pi}{k})$, of width $\frac{\pi}{k}$ and
  center $\theta$, which satisfies $\theta\pm\frac{\pi}{2k}\notin\A^k$,
  there is to any pair $(q_j,q_l)$ in $\cQ(A^0)$, which has level $k_{jl}=k$,
  exactly one direction $\alpha\in \A^k\cap I$ which satisfies, that
  $\Im(a_{jl}e^{-ik_{jl\alpha}})=0$.
  At such a direction $\alpha$, corresponding to the pair $(q_j,q_l)$, is then
  either $q_j\underset{\alpha,\max}{\prec}q_l$ or
  $q_l\underset{\alpha,\max}{\prec}q_j$ satisfied.
\end{einr}
This implies that for every $\theta$, which satisfies
$\theta\pm\frac{\pi}{2k}\notin\A^k$, is $\A^k\cap U(\theta,\frac{\pi}{k})$
a half-period and by
$\dot\bigcup_{1\leq m\leq 2k}\A^k\cap U(\theta,\frac{m\pi}{k})=\A^k$ is the
corresponding \rewrite{decomposition} in half-periods of $\A^k$ given.

Let $I=U(\theta,\frac{\pi}{k})$ be an arc width $\frac{\pi}{k}$ such that
$\theta\pm\frac{\pi}{2k}\notin\A^k$.
\begin{rem}\label{rem:remarkAboutCommonStructure}
  For every $\alpha\in\A^k\cap I$ we can write the Stokes matrix as
  \[
    K^\alpha=(K^\alpha_{jl})_{j,l\in\{1,\dots,s\}}\in\SSto_\alpha^k(A^0)
  \]
  where the $K^\alpha_{jl}\in\C^{n_j\times n_l}$ are blocks corresponding to
  the structure of $Q$ (cf.\ Definition~\ref{defn:groupOfFaithfullReps}).
  We then know for $j\neq l$ that, if $K^\alpha_{jl}\neq0$ then
  \begin{itemize}
    \item is $K^\alpha_{lj}=0$ and
    \item for every $\alpha'\in(\A^k\cap I)\backslash\{\alpha\}$ is
      $K^{\alpha'}_{jl}=0$ as well as $K^{\alpha'}_{lj}=0$.
  \end{itemize}
\end{rem}
\begin{rem}
  In the situation of Remark~\ref{rem:remarkAboutCommonStructure}
  there exists a common (block) permutation matrix $P\in\GL_n(\C)$ given by
  $(P)_{jl}=\bdelta_{\pi(j)l}$ where
  \begin{itemize}
    \item $\bdelta_{jl}$ is the block version of Kronecker's delta
      which was introduced in Definition~\ref{defn:groupOfFaithfullReps} and
    \item $\pi$ is the permutation of $\{1,\dots,s\}$ corresponding to
      $q_j\underset{\theta}{\prec}q_l$ \Leftrightarrow{} $\pi(j)<\pi(l)$
      \marginnote{\cite[18]{boalch}}
  \end{itemize}
  such that every matrix $P^{-1}K^{\alpha}P$ is upper triangular and the
  observation from remark~\ref{rem:remarkAboutCommonStructure} is still
  satisfied.
  \begin{s-rem}
    After moving the sector $U(\theta,\frac{\pi}{k})$ to
    $U(\theta,\frac{\pi}{k})+\frac{\pi}{k}
    =U(\theta+\frac{\pi}{k},\frac{\pi}{k})$ we obtain also a corresponding
    permutation $\pi'$ which is inverse to $\pi$.
    The corresponding permutation matrix $P'$ is then given by $P'=P^{-1}$.

    Such that the permutation $P$ transforms Stokes matrices on the sector
    $I+\frac{\pi}{k}$ to lower triangular matrices
  \end{s-rem}
  In the single leveled case of this phenomenon is discussed on page 18 of
  Boalch's paper~\cite{boalch}.
\end{rem}

In the paper \cite{BJL1979Birkhoff} from Balser, Jurkat and Lutz is the
following Lemma stated as Lemma 2 on page 75.
\begin{lem}\label{lem:UniqueDecompositionWotBlocks}
  Let $T\subset\{1,\dots,n\}\times\{1,\dots,n\}$ be a position set, which
  satisfies the \emph{completeness property}:
  \begin{einr}
    if $(j,k)$ and $(k,l)\in T$ then is also $(j,l)\in T$.
  \end{einr}
  Choose a indexing $i:\{1,\dots,
  \underset{\#T}{\underset{\text{\rotatebox[origin=c]{-90}{$=$}}}{\mu}}\}
  \overset{\cong}{\to}T$ of the position set and denote by
  $\delta_{jl}\in\C$ the \rewrite{ordinary} Kronecker's delta,
  then there exists for every
  \[
    K\in \left\{K=(K_{jl})_{j,l\in\{1,\dots,n\}}\in\GL_n(\C)\mid
      K_{jl}=\delta_{jl} \text{~unless~} (j,l)\in T \right\}
  \]
  unique scalars $t_j\in\C$ such that
  \[
    K=(\id + t_1E_{i(1)})\cdots(\id + t_{\mu}E_{i(\mu)}) \,.
  \]
  \begin{s-rem}
    The completeness property is reasonable, since for example
    $S_{\{(2,3),(3,2)\}}$, corresponding to the not complete set
    $\{(2,3),(3,2)\}$, is not stable under the product:
    \begin{align*}
      \begin{pmatrix}
        1 & a & 0
      \\0 & 1 & 0
      \\0 & 0 & 1
      \end{pmatrix}
      \begin{pmatrix}
        1 & 0 & 0
      \\0 & 1 & b
      \\0 & 0 & 1
      \end{pmatrix}
      =
      \begin{pmatrix}
        1 & a & \textcolor{red!60!black}{ab}
      \\0 & 1 & b
      \\0 & 0 & 1
      \end{pmatrix}
      \notin S_{\{(2,3),(3,2)\}}
      \,.
    \end{align*}
  \end{s-rem}
\end{lem}
\begin{lem}
  Every position set, corresponding to some block, is complete.
\end{lem}
\begin{proof}
  Such a position set, corresponding to some block, is given by
  \[
    T=\{(j,l)\mid j_1\leq j\leq j_2, l_1\leq l\leq l_2\}
  \]
  for some $j_1,j_2,l_2$ and $l_2$ in $\{1,\dots,n\}$.

  Let $(j,k)$, $(k,l)\in T$ be two positions.
  It is obvious that $(j,l)\in T$, since $j_1\leq j\leq j_2$ and
  $l_1\leq l\leq l_2$ are satisfied.
\end{proof}
\begin{cor}
  We can write the lemma~\ref{lem:UniqueDecompositionWotBlocks} in block form,
  corresponding to the structure of $Q$.
  Let $T\subset\{1,\dots,s\}\times\{1,\dots,s\}$ be a position set and choose a
  indexing
  \[
    i:\{1,\dots, \underset{\#T}{\underset{%
      \text{\rotatebox[origin=c]{-90}{$=$}}}{\mu}}\}\overset{\cong}{\to}T
  \]
  of $T$.
  \begin{s-defn}
    Define the group of matrices, corresponding by a complete position set, by
    \[
      S_T:=\left\{K=(K_{jl})_{j,l\in\{1,\dots,n\}}\in\GL_n(\C)\mid
      K_{jl}=\bdelta_{jl} \text{~unless~} (j,l)\in T \right\} \,,
    \]
    where $\bdelta_{jl}$ is the block version of Kronecker's delta,
    corresponding to the structure of $Q$.
  \end{s-defn}
  From the lemma~\ref{lem:UniqueDecompositionWotBlocks} then follows that for
  every $K\in S_T$ is the decomposition
  \[
    K=K_1\cdot K_2\cdots K_\mu \,,
  \]
  where $K_j\in S_{\{i(j)\}}$, is unique.
\end{cor}
From the previous corollary we deduce the following corollary.
\begin{cor}\label{cor:composeLevelwise}
  Let $T_1,\dots,T_r\subset\{1,\dots,s\}\times\{1,\dots,s\}$ be a distinct
  position sets, such that
  \begin{einr}
    $T:=T_1\dot\cup\dots\dot\cup T_r$ \rewrite{as well as} every $T_m$ satisfy
    the completeness property.
  \end{einr}
  Then is by
  \begin{align*}
    S_{T_1}\times\cdots\times S_{T_m} &\longrightarrow S_T
  \\(K_1,\dots,K_m) &\longmapsto K_1\cdots K_m
  \end{align*}
  an isomorphism defined.
\end{cor}
We can apply the previous corollary in our situation. This yields the following
theorem.
\begin{thm}
  Let $\theta\in S^1$ be a fixed direction which satisfies
  $\theta\pm\frac{\pi}{2k}\notin\A^k$, then
  \[
    \cH(A^0)\cong\prod_{k\in\cK}\prod_{j\in\{1,\dots,2k\}}
    \hat\Sto_{\theta+j\frac{\pi}{k}}^k(A^0) \,,
  \]
  where
  \begin{align*}
    \hat\SSto_{\theta}^k(A^0)
    :\!\!&= \left\{K=(K_{jl})_{j,l\in\{1,\dots,s\}}\in\GL_n(\C)\mid
        K_{jl}=\delta_{jl} \text{~unless~}
        q_j \underset{\theta}{\prec} q_l \text{, } k_{jl}=k\right\}
    \\&=S_{\{(j,l) \mid q_j \underset{\theta}{\prec} q_l \}}
  \end{align*}
  and
  \[
    \hat\Sto_{\theta}^k(A^0):=\{\rho_\theta^{-1}(K)
      \mid K\in\hat\SSto_{\theta}^k(A^0) \} \,.
  \]
  \begin{s-rem}
    \begin{enumerate}
      \item This means that the information of all Stokes-matrices on every
        level $k\in\cK$ can be grouped into $2k$ matrices, which are products
        of the corresponding Stokes matrices.
      \item By the definition above, it is obvious that
        \[
          \Sto_{\theta}^k(A^0)=
          \bigcap_{\theta'\in \A^k\cap U(\theta,\frac{\pi}{k})}
          \hat\Sto_{\theta'}^k(A^0) \,.
        \]
    \end{enumerate}
  \end{s-rem}
\end{thm}
\begin{proof}
  We have an isomorphism
  \[ \begin{tikzcd}
    \eta_\theta^k:
    \underset{\alpha\in\A^k\cap U(\theta,\frac{\pi}{k})}\prod
    \underset{S_{\{(j,l)\mid q_j\underset{\alpha,\max}{\prec}q_l\}}}{%
      \underset{\text{\rotatebox[origin=c]{-90}{$=$}}}{\underbrace{%
          \SSto_\alpha^k(A^0)}}}
    \rar{\cong}&
    \underset{S_{\{(j,l) \mid q_j \underset{\theta}{\prec} q_l \}}}{%
      \underset{\text{\rotatebox[origin=c]{-90}{$=$}}}{\underbrace{%
          \hat\SSto_\theta^k(A^0)}}}
    \,.
  \end{tikzcd} \]
  from Corollary~\ref{cor:composeLevelwise}, since
  \begin{itemize}
    \item for every $\alpha\in\A$ satisfies the set
      $\{(j,l)\mid q_j\underset{\alpha,\max}{\prec}q_l\}$ the completeness
      property, since it is defined via a \rewrite{transitiv relation}, and
    \item the union of all $\{(j,l)\mid q_j\underset{\alpha,\max}{\prec}q_l\}$
      for $\alpha\in I\cap\A^k$ is then
      \begin{align*}
        \dot\bigcup_{\alpha\in I\cap\A}
          \{(j,l)\mid q_j\underset{\alpha,\max}{\prec}q_l\}
          &=\{(j,l) \mid q_j \underset{\alpha,\max}{\prec} q_l
            \text{~for some~}\alpha\in\A^k\cap U(\theta,\frac{\pi}{k}) \}
        \\&= \{(j,l) \mid q_j \underset{\theta}{\prec} q_l \}
          \qquad\qquad\text{(cf.\ Remark~\ref{rem:relationDistanceCondition})}
      \end{align*}
      and is also complete, since $\underset{\theta}{\prec}$ is also a
      \rewrite{transitive relation}.
  \end{itemize}
  The isomorphism of the theorem is then the Stokes germ version of
  \[ \begin{tikzcd}
    \underset{\eta}{%
      \underset{\text{\rotatebox[origin=c]{90}{$:=$}}}{\underbrace{%
        \underset{k\in\cK}{\prod}\underset{j\in\{1,\dots,2k\}}{\prod}
        \eta_{\theta+j\frac{\pi}{k}}^k
    }}}:
    \underset{\cH(A^0)}{%
      \underset{\text{\rotatebox[origin=c]{-90}{$\cong$}}}{\underbrace{%
        \prod_{k\in\cK}\prod_{\alpha\in\A^k}\SSto_\alpha^k(A^0)}}}
    \rar{\cong}&
    \underset{k\in\cK}{\prod}\underset{j\in\{1,\dots,2k\}}{\prod}
    \hat\SSto_{\theta+j\frac{\pi}{k}}^k(A^0) \,.
  \end{tikzcd} \]
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The complete Diagram}\label{sec:theCompleteDiagram}
If we start with the diagram from page~\pageref{page:ofPreDiagram}, we can add
all the defined isomorphisms and rewrite into the following diagram.
\begin{center}
  \begin{tikzpicture}
    \pgfmathsetmacro{\dx}{4cm}
    \pgfmathsetmacro{\ldx}{6cm}
    \pgfmathsetmacro{\dy}{2.5cm}
    \pgfmathsetmacro{\mdy}{-1.5cm}

    \node (cH) at (-6,3.5) {$\cH(A^0)$};
    \node (ProdOfStos) at (-6,-4)
      {$\displaystyle\prod_{\alpha\in\A}\Sto_{\alpha}(A^0)$};
    \node (S3P) at ([xshift={\dx},yshift={\dy}]ProdOfStos)
      {$\displaystyle\prod_{k\in\cK}\prod_{\alpha\in\A}\Sto_{\alpha}^{k}(A^0)$};
    \node (S2P) at ([xshift={\dx},yshift={\dy}]S3P)
      {$\displaystyle\prod_{k\in\cK}\Gamma(\dot\cU^k;\Lambda^k(A^0))$};
    \node (StA0) at ([xshift={\dx},yshift={\dy}]S2P)
      {$\St(A^0)$};
    \node (ProdOfSStos) at ([yshift=-{\dy}]ProdOfStos)
      {$\displaystyle\prod_{\alpha\in\A}\SSto_{\alpha}(A^0)$};
    \node (SS3P) at ([yshift=-{\dy}]S3P)
      {$\displaystyle\prod_{k\in\cK}\prod_{\alpha\in\A}\SSto_{\alpha}^{k}(A^0)$};
    \node (SS2P) at ([yshift={\mdy},xshift={\ldx}]S3P)
      {$\displaystyle\prod_{k\in\cK} \prod_{j\in\{1,\dots,2k\}}
        \hat\Sto_{\theta+j\frac{\pi}{k}}^k(A^0)$};
    \node (SSS2P) at ([yshift={\mdy},xshift={\ldx}]SS3P)
      {$\displaystyle\prod_{k\in\cK} \prod_{j\in\{1,\dots,2k\}}
        \hat\SSto_{\theta+j\frac{\pi}{k}}^k(A^0)$};
    \node[red] (SSS3P) at ([yshift={\mdy},xshift={\ldx}]ProdOfSStos)
      {$\displaystyle\prod_{\alpha\in\A}
        \C^{\sum_{q_j\underset{\alpha,\max}{\prec}q_l}
          \deg(q_j-q_l)\cdot n_j\cdot n_l}$};

    \draw[->] (cH) -- (ProdOfStos)
      node[midway,left] {$g$};
    \draw[->] (cH) -- (StA0)
      node[midway,above] {$\exp_{A^0}$};
    \draw[->,purple] (ProdOfStos) -- (S3P)
      node[midway,above left] {\rewrite{$\displaystyle\chi\circ\prod_{\alpha\in\A}i_\alpha$}};
    \draw[->,purple] (S3P) -- (S2P)
      node[midway,above left] {$\prod_{k\in\cK}i^k$};
    \draw[->,purple] (S2P) -- (StA0)
      node[midway,above left] {$\cT$};
    \draw[->] (ProdOfStos) -- (ProdOfSStos)
      node[midway,left] {$\prod_{\alpha\in\A}\rho_\alpha$};
    \draw[->] (ProdOfSStos) -- (SS3P)
      node[midway,below right] {\rewrite{$\displaystyle\chi\circ\prod_{\alpha\in\A}i_\alpha$}};
    \draw[->] (S3P) -- (SS3P)
      node[midway,right] {$\prod_{k\in\cK}\prod_{\alpha\in\A}\rho_{\alpha}^k$};
    \draw[->] (S3P) -- (SS2P)
      node[midway] {};
    \draw[->] (SS3P) -- (SSS2P)
      node[midway,above] {$\eta$};
    \draw[->] (SS2P) -- (SSS2P)
      node[midway,right] {(induced by $\rho$)};
    \draw[->,red] (SSS3P) -- (ProdOfSStos)
      node[midway,below left,red] {Cor.\ref{cor:isomToChochN}};
  \end{tikzpicture}
\end{center}
Where
\begin{itemize}
  \item the \textcolor{purple}{purple path} is the isomorphism $h$ from
    theorem~\ref{thm:mainThm2} and
  \item we denote
    \begin{itemize}
      \item $\chi:\displaystyle \prod_{\alpha\in\A}\prod_{k\in\cK}\Sto_\alpha^k(A^0)
        \equiv\displaystyle \prod_{k\in\cK}\prod_{\alpha\in\A}\Sto_\alpha^k(A^0)$
        the reordering and
      \item by abuse of notation we also denote the Stokes matrix version in
        the same way
        $\chi:\displaystyle \prod_{\alpha\in\A}\prod_{k\in\cK}\SSto_\alpha^k(A^0)
        \equiv\displaystyle
        \prod_{k\in\cK}\prod_{\alpha\in\A}\SSto_\alpha^k(A^0)$.
    \end{itemize}
\end{itemize}
\PROBLEM[Der unterste respektiert die Struktur nicht]
